---
title: "Calling TBI data"
author: "Hunter Ratliff"
date: "2/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=F, warning=F)
library(tidyverse)
library(glue)
```

## Original county

```{r cars}
TBIs_org <- read_csv("Data/TBI_Deaths.csv") %>%
  # Correct Shannon, SD to it's new name
  mutate(
    CountyFIPS = ifelse(CountyFIPS=="46113", "46102", CountyFIPS),
    County     = ifelse(CountyFIPS=="46102", "OGLALA LAKOTA", County))
```

# OVERALL

Traumatic Brain Injury, All Intents, All Races, All Ethnicities, Both Sexes, All Ages

```{r overall-county}
url <- "https://wisqars.cdc.gov:8443/cdcMapFramework/ExcelServlet?excelFile=m8976144_csv"
table.name <- read_csv(url)[[4,1]]
table.id   <- read_csv(url)[[11,1]]
pop.subset <- "Overall"


df <- read_csv(url, skip = 21) %>%
  # Make FIPS
  mutate(StateFIPS  = str_pad(StateFIPS, pad = "0", width = 2),
         CountyFIPS = str_pad(CountyFIPS, pad = "0", width = 3),
         GEOID      = str_c(StateFIPS, CountyFIPS)) %>%
  
  # Correct county data
  mutate(CountyFIPS = ifelse(CountyFIPS=="46113", "46102", CountyFIPS),
         County     = ifelse(CountyFIPS=="46102", "OGLALA LAKOTA", County)) %>%
  
  # Re-arrange order
  select(GEOID, ST, County, StdPop=Population, Deaths, Crude=U_C_Rate, AgeAdj=U_A_Rate) %>%
  
  # Add tag columns
  mutate(pop.subset = pop.subset,
         geo.level  = "county",
         table.id   = table.id,
         table.name = table.name)

View(df)
df %>% write_csv(glue("TBI_data/County/TBI_{pop.subset}_county.csv"))
rm(url, table.name, table.id, pop.subset)
```

```{r overall-state}
url <- "https://wisqars.cdc.gov:8443/cdcMapFramework/ExcelServlet?excelFile=m2106188_csv"
table.name <- read_csv(url)[[4,1]]
table.id   <- read_csv(url)[[11,1]]
pop.subset <- "Overall"

df <- read_csv(url, skip = 21) %>%
  
  # Re-arrange order
  select(ST, StdPop_ST=Population, Deaths_ST=Deaths, Crude_ST=U_C_Rate, AgeAdj_ST=U_A_Rate) %>%
  
  # Add tag columns
  mutate(pop.subset = pop.subset,
         geo.level  = "state",
         table.id   = table.id,
         table.name = table.name)

View(df)
df %>% write_csv(glue("TBI_data/State/TBI_{pop.subset}_state.csv"))
rm(url, table.name, table.id, pop.subset)
```

# By sex

## Males only

Traumatic Brain Injury, All Intents, All Races, All Ethnicities, **Males**, All Ages

```{r males-county}
url <- "https://wisqars.cdc.gov:8443/cdcMapFramework/ExcelServlet?excelFile=m7245223_csv"
table.name <- read_csv(url)[[4,1]]
table.id   <- read_csv(url)[[11,1]]
pop.subset <- "males"


df <- read_csv(url, skip = 21) %>%
  # Make FIPS
  mutate(StateFIPS  = str_pad(StateFIPS, pad = "0", width = 2),
         CountyFIPS = str_pad(CountyFIPS, pad = "0", width = 3),
         GEOID      = str_c(StateFIPS, CountyFIPS)) %>%
  
  # Correct county data
  mutate(CountyFIPS = ifelse(CountyFIPS=="46113", "46102", CountyFIPS),
         County     = ifelse(CountyFIPS=="46102", "OGLALA LAKOTA", County)) %>%
  
  # Re-arrange order
  select(GEOID, ST, County, StdPop=Population, Deaths, Crude=U_C_Rate, AgeAdj=U_A_Rate) %>%
  
  # Add tag columns
  mutate(pop.subset = pop.subset,
         geo.level  = "county",
         table.id   = table.id,
         table.name = table.name)

View(df)
df %>% write_csv(glue("TBI_data/County/TBI_{pop.subset}_county.csv"))
rm(url, table.name, table.id, pop.subset)
```

```{r males-state}
url <- "https://wisqars.cdc.gov:8443/cdcMapFramework/ExcelServlet?excelFile=m4328936_csv"
table.name <- read_csv(url)[[4,1]]
table.id   <- read_csv(url)[[11,1]]
pop.subset <- "males"

df <- read_csv(url, skip = 21) %>%
  
  # Re-arrange order
  select(ST, StdPop_ST=Population, Deaths_ST=Deaths, Crude_ST=U_C_Rate, AgeAdj_ST=U_A_Rate) %>%
  
  # Add tag columns
  mutate(pop.subset = pop.subset,
         geo.level  = "state",
         table.id   = table.id,
         table.name = table.name)

View(df)
df %>% write_csv(glue("TBI_data/State/TBI_{pop.subset}_state.csv"))
rm(url, table.name, table.id, pop.subset)
```

## Females only

Traumatic Brain Injury, All Intents, All Races, All Ethnicities, **Females**, All Ages

```{r females-county}
url <- "https://wisqars.cdc.gov:8443/cdcMapFramework/ExcelServlet?excelFile=m4010307_csv"
table.name <- read_csv(url)[[4,1]]
table.id   <- read_csv(url)[[11,1]]
pop.subset <- "females"


df <- read_csv(url, skip = 21) %>%
  # Make FIPS
  mutate(StateFIPS  = str_pad(StateFIPS, pad = "0", width = 2),
         CountyFIPS = str_pad(CountyFIPS, pad = "0", width = 3),
         GEOID      = str_c(StateFIPS, CountyFIPS)) %>%
  
  # Correct county data
  mutate(CountyFIPS = ifelse(CountyFIPS=="46113", "46102", CountyFIPS),
         County     = ifelse(CountyFIPS=="46102", "OGLALA LAKOTA", County)) %>%
  
  # Re-arrange order
  select(GEOID, ST, County, StdPop=Population, Deaths, Crude=U_C_Rate, AgeAdj=U_A_Rate) %>%
  
  # Add tag columns
  mutate(pop.subset = pop.subset,
         geo.level  = "county",
         table.id   = table.id,
         table.name = table.name)

View(df)
df %>% write_csv(glue("TBI_data/County/TBI_{pop.subset}_county.csv"))
rm(url, table.name, table.id, pop.subset)
```

```{r females-state}
url <- "https://wisqars.cdc.gov:8443/cdcMapFramework/ExcelServlet?excelFile=m2518907_csv"
table.name <- read_csv(url)[[4,1]]
table.id   <- read_csv(url)[[11,1]]
pop.subset <- "females"

df <- read_csv(url, skip = 21) %>%
  
  # Re-arrange order
  select(ST, StdPop_ST=Population, Deaths_ST=Deaths, Crude_ST=U_C_Rate, AgeAdj_ST=U_A_Rate) %>%
  
  # Add tag columns
  mutate(pop.subset = pop.subset,
         geo.level  = "state",
         table.id   = table.id,
         table.name = table.name)

View(df)
df %>% write_csv(glue("TBI_data/State/TBI_{pop.subset}_state.csv"))
rm(url, table.name, table.id, pop.subset)
```

# Ages

## 65+ years old


```{r age65-county}
url <- "https://wisqars.cdc.gov:8443/cdcMapFramework/ExcelServlet?excelFile=m7284009_csv"
table.name <- read_csv(url)[[4,1]]
table.id   <- read_csv(url)[[11,1]]
pop.subset <- "65+ year old"


df <- read_csv(url, skip = 21) %>%
  # Make FIPS
  mutate(StateFIPS  = str_pad(StateFIPS, pad = "0", width = 2),
         CountyFIPS = str_pad(CountyFIPS, pad = "0", width = 3),
         GEOID      = str_c(StateFIPS, CountyFIPS)) %>%
  
  # Correct county data
  mutate(CountyFIPS = ifelse(CountyFIPS=="46113", "46102", CountyFIPS),
         County     = ifelse(CountyFIPS=="46102", "OGLALA LAKOTA", County)) %>%
  
  # Re-arrange order
  select(GEOID, ST, County, StdPop=Population, Deaths, Crude=U_C_Rate, AgeAdj=U_A_Rate) %>%
  
  # Add tag columns
  mutate(pop.subset = pop.subset,
         geo.level  = "county",
         table.id   = table.id,
         table.name = table.name)

View(df)
df %>% write_csv(glue("TBI_data/County/TBI_{pop.subset}_county.csv"))
rm(url, table.name, table.id, pop.subset)
glue("{100*round(nrow(filter(df, is.na(Deaths)))/nrow(df),3)}% missing")
```

```{r age65-state}
url <- "https://wisqars.cdc.gov:8443/cdcMapFramework/ExcelServlet?excelFile=m3750744_csv"
table.name <- read_csv(url)[[4,1]]
table.id   <- read_csv(url)[[11,1]]
pop.subset <- "65+ year old"

df <- read_csv(url, skip = 21) %>%
  
  # Re-arrange order
  select(ST, StdPop_ST=Population, Deaths_ST=Deaths, Crude_ST=U_C_Rate, AgeAdj_ST=U_A_Rate) %>%
  
  # Add tag columns
  mutate(pop.subset = pop.subset,
         geo.level  = "state",
         table.id   = table.id,
         table.name = table.name)

View(df)
df %>% write_csv(glue("TBI_data/State/TBI_{pop.subset}_state.csv"))
rm(url, table.name, table.id, pop.subset)
```


# Intent

## Unintentional

```{r unintentional-county}
url <- "https://wisqars.cdc.gov:8443/cdcMapFramework/ExcelServlet?excelFile=m3378873_csv"
table.name <- read_csv(url)[[4,1]]
table.id   <- read_csv(url)[[11,1]]
pop.subset <- "unintentional"


df <- read_csv(url, skip = 21) %>%
  # Make FIPS
  mutate(StateFIPS  = str_pad(StateFIPS, pad = "0", width = 2),
         CountyFIPS = str_pad(CountyFIPS, pad = "0", width = 3),
         GEOID      = str_c(StateFIPS, CountyFIPS)) %>%
  
  # Correct county data
  mutate(CountyFIPS = ifelse(CountyFIPS=="46113", "46102", CountyFIPS),
         County     = ifelse(CountyFIPS=="46102", "OGLALA LAKOTA", County)) %>%
  
  # Re-arrange order
  select(GEOID, ST, County, StdPop=Population, Deaths, Crude=U_C_Rate, AgeAdj=U_A_Rate) %>%
  
  # Add tag columns
  mutate(pop.subset = pop.subset,
         geo.level  = "county",
         table.id   = table.id,
         table.name = table.name)

View(df)
df %>% write_csv(glue("TBI_data/County/TBI_{pop.subset}_county.csv"))
rm(url, table.name, table.id, pop.subset)
glue("{100*round(nrow(filter(df, is.na(Deaths)))/nrow(df),3)}% missing")
```

```{r unintentional-state}
url <- "https://wisqars.cdc.gov:8443/cdcMapFramework/ExcelServlet?excelFile=m4021328_csv"
table.name <- read_csv(url)[[4,1]]
table.id   <- read_csv(url)[[11,1]]
pop.subset <- "unintentional"

df <- read_csv(url, skip = 21) %>%
  
  # Re-arrange order
  select(ST, StdPop_ST=Population, Deaths_ST=Deaths, Crude_ST=U_C_Rate, AgeAdj_ST=U_A_Rate) %>%
  
  # Add tag columns
  mutate(pop.subset = pop.subset,
         geo.level  = "state",
         table.id   = table.id,
         table.name = table.name)

View(df)
df %>% write_csv(glue("TBI_data/State/TBI_{pop.subset}_state.csv"))
rm(url, table.name, table.id, pop.subset)
```

## Suicide

```{r suicide-county}
url <- "https://wisqars.cdc.gov:8443/cdcMapFramework/ExcelServlet?excelFile=m509846_csv"
table.name <- read_csv(url)[[4,1]]
table.id   <- read_csv(url)[[11,1]]
pop.subset <- "suicide"


df <- read_csv(url, skip = 21) %>%
  # Make FIPS
  mutate(StateFIPS  = str_pad(StateFIPS, pad = "0", width = 2),
         CountyFIPS = str_pad(CountyFIPS, pad = "0", width = 3),
         GEOID      = str_c(StateFIPS, CountyFIPS)) %>%
  
  # Correct county data
  mutate(CountyFIPS = ifelse(CountyFIPS=="46113", "46102", CountyFIPS),
         County     = ifelse(CountyFIPS=="46102", "OGLALA LAKOTA", County)) %>%
  
  # Re-arrange order
  select(GEOID, ST, County, StdPop=Population, Deaths, Crude=U_C_Rate, AgeAdj=U_A_Rate) %>%
  
  # Add tag columns
  mutate(pop.subset = pop.subset,
         geo.level  = "county",
         table.id   = table.id,
         table.name = table.name)

View(df)
df %>% write_csv(glue("TBI_data/County/TBI_{pop.subset}_county.csv"))
rm(url, table.name, table.id, pop.subset)
glue("{100*round(nrow(filter(df, is.na(Deaths)))/nrow(df),3)}% missing")
```

```{r suicide-state}
url <- "https://wisqars.cdc.gov:8443/cdcMapFramework/ExcelServlet?excelFile=m8496524_csv"
table.name <- read_csv(url)[[4,1]]
table.id   <- read_csv(url)[[11,1]]
pop.subset <- "suicide"

df <- read_csv(url, skip = 21) %>%
  
  # Re-arrange order
  select(ST, StdPop_ST=Population, Deaths_ST=Deaths, Crude_ST=U_C_Rate, AgeAdj_ST=U_A_Rate) %>%
  
  # Add tag columns
  mutate(pop.subset = pop.subset,
         geo.level  = "state",
         table.id   = table.id,
         table.name = table.name)

View(df)
df %>% write_csv(glue("TBI_data/State/TBI_{pop.subset}_state.csv"))
rm(url, table.name, table.id, pop.subset)
```

# Mechanism

## Transportation

```{r transportation-county}
url <- "https://wisqars.cdc.gov:8443/cdcMapFramework/ExcelServlet?excelFile=m3529311_csv"
table.name <- read_csv(url)[[4,1]]
table.id   <- read_csv(url)[[11,1]]
pop.subset <- "transportation"


df <- read_csv(url, skip = 21) %>%
  # Make FIPS
  mutate(StateFIPS  = str_pad(StateFIPS, pad = "0", width = 2),
         CountyFIPS = str_pad(CountyFIPS, pad = "0", width = 3),
         GEOID      = str_c(StateFIPS, CountyFIPS)) %>%
  
  # Correct county data
  mutate(CountyFIPS = ifelse(CountyFIPS=="46113", "46102", CountyFIPS),
         County     = ifelse(CountyFIPS=="46102", "OGLALA LAKOTA", County)) %>%
  
  # Re-arrange order
  select(GEOID, ST, County, StdPop=Population, Deaths, Crude=U_C_Rate, AgeAdj=U_A_Rate) %>%
  
  # Add tag columns
  mutate(pop.subset = pop.subset,
         geo.level  = "county",
         table.id   = table.id,
         table.name = table.name)

View(df)
df %>% write_csv(glue("TBI_data/County/TBI_{pop.subset}_county.csv"))
rm(url, table.name, table.id, pop.subset)
glue("{100*round(nrow(filter(df, is.na(Deaths)))/nrow(df),3)}% missing")
```

```{r transportation-state}
url <- "https://wisqars.cdc.gov:8443/cdcMapFramework/ExcelServlet?excelFile=m8177371_csv"
table.name <- read_csv(url)[[4,1]]
table.id   <- read_csv(url)[[11,1]]
pop.subset <- "transportation"

df <- read_csv(url, skip = 21) %>%
  
  # Re-arrange order
  select(ST, StdPop_ST=Population, Deaths_ST=Deaths, Crude_ST=U_C_Rate, AgeAdj_ST=U_A_Rate) %>%
  
  # Add tag columns
  mutate(pop.subset = pop.subset,
         geo.level  = "state",
         table.id   = table.id,
         table.name = table.name)

View(df)
df %>% write_csv(glue("TBI_data/State/TBI_{pop.subset}_state.csv"))
rm(url, table.name, table.id, pop.subset)
```

## Fall

```{r fall-county}
url <- "https://wisqars.cdc.gov:8443/cdcMapFramework/ExcelServlet?excelFile=m4794739_csv"
table.name <- read_csv(url)[[4,1]]
table.id   <- read_csv(url)[[11,1]]
pop.subset <- "fall"


df <- read_csv(url, skip = 21) %>%
  # Make FIPS
  mutate(StateFIPS  = str_pad(StateFIPS, pad = "0", width = 2),
         CountyFIPS = str_pad(CountyFIPS, pad = "0", width = 3),
         GEOID      = str_c(StateFIPS, CountyFIPS)) %>%
  
  # Correct county data
  mutate(CountyFIPS = ifelse(CountyFIPS=="46113", "46102", CountyFIPS),
         County     = ifelse(CountyFIPS=="46102", "OGLALA LAKOTA", County)) %>%
  
  # Re-arrange order
  select(GEOID, ST, County, StdPop=Population, Deaths, Crude=U_C_Rate, AgeAdj=U_A_Rate) %>%
  
  # Add tag columns
  mutate(pop.subset = pop.subset,
         geo.level  = "county",
         table.id   = table.id,
         table.name = table.name)

View(df)
df %>% write_csv(glue("TBI_data/County/TBI_{pop.subset}_county.csv"))
rm(url, table.name, table.id, pop.subset)
glue("{100*round(nrow(filter(df, is.na(Deaths)))/nrow(df),3)}% missing")
```

```{r fall-state}
url <- "https://wisqars.cdc.gov:8443/cdcMapFramework/ExcelServlet?excelFile=m7228039_csv"
table.name <- read_csv(url)[[4,1]]
table.id   <- read_csv(url)[[11,1]]
pop.subset <- "fall"

df <- read_csv(url, skip = 21) %>%
  
  # Re-arrange order
  select(ST, StdPop_ST=Population, Deaths_ST=Deaths, Crude_ST=U_C_Rate, AgeAdj_ST=U_A_Rate) %>%
  
  # Add tag columns
  mutate(pop.subset = pop.subset,
         geo.level  = "state",
         table.id   = table.id,
         table.name = table.name)

View(df)
df %>% write_csv(glue("TBI_data/State/TBI_{pop.subset}_state.csv"))
rm(url, table.name, table.id, pop.subset)
```

## Firearm

```{r firearm-county}
url <- "https://wisqars.cdc.gov:8443/cdcMapFramework/ExcelServlet?excelFile=m6453951_csv"
table.name <- read_csv(url)[[4,1]]
table.id   <- read_csv(url)[[11,1]]
pop.subset <- "firearm"


df <- read_csv(url, skip = 21) %>%
  # Make FIPS
  mutate(StateFIPS  = str_pad(StateFIPS, pad = "0", width = 2),
         CountyFIPS = str_pad(CountyFIPS, pad = "0", width = 3),
         GEOID      = str_c(StateFIPS, CountyFIPS)) %>%
  
  # Correct county data
  mutate(CountyFIPS = ifelse(CountyFIPS=="46113", "46102", CountyFIPS),
         County     = ifelse(CountyFIPS=="46102", "OGLALA LAKOTA", County)) %>%
  
  # Re-arrange order
  select(GEOID, ST, County, StdPop=Population, Deaths, Crude=U_C_Rate, AgeAdj=U_A_Rate) %>%
  
  # Add tag columns
  mutate(pop.subset = pop.subset,
         geo.level  = "county",
         table.id   = table.id,
         table.name = table.name)

View(df)
df %>% write_csv(glue("TBI_data/County/TBI_{pop.subset}_county.csv"))
rm(url, table.name, table.id, pop.subset)
glue("{100*round(nrow(filter(df, is.na(Deaths)))/nrow(df),3)}% missing")
```

```{r firearm-state}
url <- "https://wisqars.cdc.gov:8443/cdcMapFramework/ExcelServlet?excelFile=m6384422_csv"
table.name <- read_csv(url)[[4,1]]
table.id   <- read_csv(url)[[11,1]]
pop.subset <- "firearm"

df <- read_csv(url, skip = 21) %>%
  
  # Re-arrange order
  select(ST, StdPop_ST=Population, Deaths_ST=Deaths, Crude_ST=U_C_Rate, AgeAdj_ST=U_A_Rate) %>%
  
  # Add tag columns
  mutate(pop.subset = pop.subset,
         geo.level  = "state",
         table.id   = table.id,
         table.name = table.name)

View(df)
df %>% write_csv(glue("TBI_data/State/TBI_{pop.subset}_state.csv"))
rm(url, table.name, table.id, pop.subset)
```