---
title: "Loading data"
author: "Hunter Ratliff"
date: "1/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=F, warning=F, message=F)

library(spdep)
library(sp)
library(tigris)
library(leaflet)
library(tidycensus)
library(tidyverse)
library(ggmap)
library(viridis)
library(tictoc)
library(RColorBrewer)
library(rgeos)
```

```{r tigrisFiles}
options(tigris_use_cache = TRUE)
sf_county <- tigris::counties()
# sf_zip    <- tigris::zctas(cb=F)
```

```{r getACS, echo=F}
population <- tidycensus::get_acs(geography = "county", shift_geo = T,
                                  variables = "B01001_001", geometry = T)
population_leaflet <- tidycensus::get_acs(geography = "county", # don't shift
                                  variables = "B01001_001", geometry = T)
```

```{r traumaCenters}
traumaCenters <- read_csv("Data/TraumaCenters.csv")
```

```{r read_TBI}
TBIs <- read_csv("Data/TBI_Deaths.csv")
```





# Load the NPI data

We're grabbing data from the 2017 [Medicare Provider Utilization and Payment Data: Physician and Other Supplier](https://www.cms.gov/Research-Statistics-Data-and-Systems/Statistics-Trends-and-Reports/Medicare-Provider-Charge-Data/Physician-and-Other-Supplier2017). This data can be downloaded from this page, but contains over 9 million records and is 2 GB unzipped.

The code chunk below downloads the whole dataset (`rawdata`), subsets it to select only neurosurgeons (`raw_NSG`) and writes that subset to a CSV. Because the full dataset is so large I only run this step once, and all future code will rely on `raw_NSG.csv`

```{r loadFullData, eval=F}
## Using RSocrata
rawdata <- "https://data.cms.gov/resource/fs4p-t5eq.csv" %>%
  read.socrata() %>%
  as_tibble()
beepr::beep()



## Using downloaded file
file_location <- paste0("~/Downloads/Medicare_Provider_Util_Payment_PUF_CY2017/",
                        "Medicare_Provider_Util_Payment_PUF_CY2017.txt")

rawdata <- readr::read_delim(file_location, "\t", escape_double=F, trim_ws=T)
rm(file_location)



## Select only Neurosurgery
raw_NSG <- rawdata  %>% 
  filter(npi!="0000000001") %>%
  filter(provider_type=="Neurosurgery") %>%
  rename(street=nppes_provider_street1, city=nppes_provider_city, 
         state=nppes_provider_state, country=nppes_provider_country,
         zip=nppes_provider_zip,
         
         lastName=nppes_provider_last_org_name,
         firstName=nppes_provider_first_name,
         gender=nppes_provider_gender) %>%
  select(-nppes_provider_mi, -nppes_provider_street2) %>%
  mutate(zip = str_trunc(zip, 5, "right", ellipsis = ""))

write_csv(raw_NSG, "Data/raw_NSG.csv")
rm(rawdata, raw_NSG)
```

```{r read_NSG}
NSG <- read_csv("Data/raw_NSG.csv") %>%
  rename(degree=nppes_credentials) %>%
  mutate(degree = str_replace_all(degree, "\\.","")) %>%
  
  # Rename vars
  rename(drug=hcpcs_drug_indicator,
         accptMedicare=medicare_participation_indicator,
         
         num.services       = line_srvc_cnt,
         num.bene_uniq      = bene_unique_cnt,
         avg.allowed_amt    = average_Medicare_allowed_amt,
         avg.submitted_chrg = average_submitted_chrg_amt,
         avg.paid           = average_Medicare_payment_amt,
         avg.paid_std       = average_Medicare_standard_amt) %>%
  
  # Select only relevant vars
  select(-nppes_entity_code, -provider_type,
         -bene_day_srvc_cnt) %>%
  select(npi:gender, accptMedicare:avg.paid_std)
```


# Geocoding

```{r callGeocoding, eval=F}
sf_zip    <- tigris::zctas(cb=F)


## Function to take coordinates, and return the name of the county
latlong2county <- function(long, lat) {
  library(sp)
  library(maps)
  library(maptools)
  # Prepare SpatialPolygons object with one SpatialPolygon
  # per county
  counties <- map('county', fill=TRUE, col="transparent", plot=FALSE)
  IDs <- sapply(strsplit(counties$names, ":"), function(x) x[1])
  counties_sp <- map2SpatialPolygons(counties, IDs=IDs,
                                     proj4string=CRS("+proj=longlat +datum=WGS84"))
  
  # Convert pointsDF to a SpatialPoints object 
  pointsSP <- SpatialPoints(data.frame(long=long, lat=lat), 
                            proj4string=CRS("+proj=longlat +datum=WGS84"))
  
  # Use 'over' to get _indices_ of the Polygons object containing each point 
  indices <- over(pointsSP, counties_sp)
  
  # Return the county names of the Polygons object containing each point
  countyNames <- sapply(counties_sp@polygons, function(x) x@ID)
  countyNames[indices]
}

raw_NSG <- read_csv("Data/raw_NSG.csv")

geocoded <- raw_NSG %>%
  select(npi, street, city, state, zip) %>%
  unique() %>%
  left_join(select(sf_zip@data, zip=GEOID10, lat=INTPTLAT10, lon=INTPTLON10)) %>%
  mutate(
    lat = as.numeric(lat),
    lon = as.numeric(lon)
  )

geocoded_missing <- geocoded %>%
  filter(is.na(lat)|is.na(lon)) %>%
  mutate(address = glue::glue("{city}, {state}, {zip}")) %>%
  select(npi, address) %>%
  unique()

google_geocoded <- geocoded_missing %>%
  select(address) %>%
  unique() %>%
  mutate_geocode(address, output="more")


# Re-write `geocoded` with missing values filled in
geocoded <- left_join(geocoded_missing, google_geocoded) %>%
  right_join(
    select(filter(geocoded, is.na(lat)|is.na(lon)), -lon, -lat)
  ) %>%
  mutate(zip=NA) %>%
  select(npi, street, city, state, zip, lat, lon) %>%
  bind_rows(.,
    filter(geocoded, !is.na(lat), !is.na(lon))
  )
rm(geocoded_missing, google_geocoded)





geocoded2 <- geocoded %>%
  mutate(county_name = latlong2county(lon, lat)) %>%
  left_join(
    {county.fips %>%
      rename(county_name=polyname, county_FIPS=fips) %>%
      mutate(county_name = str_replace(county_name, ":.*", "")) %>%
      unique()}
    )


tictoc::tic("Calling cenus")
missing_geoid <- geocoded2 %>%  # takes a little over 1 min
  filter(is.na(county_FIPS)) %>%
  append_geoid(geoid_type = "county") %>%
  mutate(county_FIPS=geoid)
tictoc::toc()
beepr::beep()

geo_final <- bind_rows(
  select(missing_geoid, -geoid),
  mutate(filter(geocoded2, !is.na(county_FIPS)), county_FIPS=as.character(county_FIPS))
) %>%
  mutate(county_FIPS=str_pad(county_FIPS, 5, pad="0"))

write_csv(geo_final, "geocode_npi.csv")
rm(geocoded, missing_geoid, geocoded2, latlong2county)
```


```{r readraw_NSG}
geo_npi <- read_csv("Data/geocode_npi.csv")
```


# Create datasets

## Services

- **NPI**
- **accptMedicare**
- **place_of_service**: Identifies whether the place of service submitted on the claims is a facility (value of ‘F’) or non-facility (value of ‘O’). Non-facility is generally an office setting
- **hcpcs_code**: Healthcare Common Procedure Coding System (HCPCS) code for the specific medical service furnished by the provider
- **hcpcs_description**: Description of the HCPCS code for the specific medical service furnished by the provider. HCPCS descriptions associated with CPT codes are consumer friendly descriptions provided by the AMA.
- **drug**: Identifies whether the HCPCS code for the specific service furnished by the provider is a HCPCS listed on the Medicare Part B Drug Average Sales Price (ASP) File
- **num.services**: Number of services provided; note that the metrics used to count the number provided can vary from service to service
- **num.bene_uniq**: Number of distinct Medicare beneficiaries receiving the service.
- **avg.allowed_amt**: Average of the Medicare allowed amount for the service; _this figure is the sum of the amount Medicare pays, the deductible and coinsurance amounts that the beneficiary is responsible for paying, and any amounts that a third party is responsible for paying._
- **avg.submitted_chrg**: Average of the charges that the provider submitted for the service.
- **avg.paid**: Average amount that Medicare paid after deductible and coinsurance amounts have been deducted for the line item service
- **avg.paid_std**: Average amount that Medicare paid after beneficiary deductible and coinsurance amounts have been deducted for the line item service and after standardization of the Medicare payment has been applied.

```{r}
services <- NSG %>% select(npi, accptMedicare:avg.paid_std)
```

## Providers

```{r}
providers <- NSG %>%
  group_by(npi, place_of_service) %>%
  summarise(srvc_uniq = sum(num.bene_uniq)) %>%
  spread(place_of_service, srvc_uniq, fill = 0) %>%
  rename(inpatient=`F`, office=`O`) %>%
  
  # Join to rest of npi data
  right_join(unique(select(NSG, npi:gender))) %>%
  
  left_join(geo_npi)

# colSums(is.na(providers))
```


# Maps




```{r basicMap}
df <-  population %>%
  # filter(!str_detect(GEOID, "72..."), !str_detect(GEOID, "02..."),
  #        !str_detect(GEOID, "15...")) %>%
  filter(!str_detect(GEOID, "72...")) %>%
  select(GEOID, NAME, population=estimate, geometry) %>%
  left_join(., by=c("GEOID"="county_FIPS"),
    summarise(group_by(providers, county_FIPS), NPIs=n())) %>%
  
  mutate(Ratio = NPIs*100000/population) %>%
  mutate(Ratio_bin = cut(Ratio, c(0:2, 4, 6, Inf),
                         right=F)) 


df %>%
  filter(!is.na(NPIs)) %>%
  # mutate(Ratio = ifelse(Ratio>7, 7, Ratio)) %>%

  ggplot(aes(x=Ratio_bin, fill=Ratio_bin)) +
  geom_bar()
  geom_histogram()
  



tictoc::tic("Start plot")

df %>% # per 100,000 population
  
  ggplot(aes(fill = Ratio_bin)) +
  geom_sf() +
  coord_sf(crs = 26914) +
  scale_fill_brewer(palette="PiYG", na.value="grey50", direction=1,
                    name="Ratio Per 100k") +
  theme(legend.direction="horizontal",legend.position=c(0.5,0))
  # scale_fill_gradientn(colours = terrain.colors(5), na.value = "grey50")
tictoc::toc()
```


# Injury data

Using the CDC's WISQARS database, I downloaded the **age-adjusted rates** per 100,000 Population for each county of fatal TBI injuries (all intents, all mechanisms, all ages, all race/ethnicity, both sexes) from 2008-2014. It's based on the 2000 standard population (all races, both sexes). Data was downloaded on 1/17/2020

Produced by: the Statistics, Programming & Economics Branch, National Center for Injury Prevention & Control, CDC    
Data Sources: NCHS National Vital Statistics System for numbers of deaths; US Census Bureau for population estimates

```{r}
TBIs <- read_csv("Data/TBI_Deaths.csv")
  # mutate(
  #   AgeAdj_Rate = scales::squish(AgeAdj_Rate, range = c(0,50)),
  #   Crude_Rate  = scales::squish(Crude_Rate, range = c(0,50))
  # ) 
```

The distribution of the rates of TBIs has a few outliers, including McKenzie County, ND

```{r}
# TBIs %>%
#   mutate(
#     AgeAdj_Rate = scales::squish(AgeAdj_Rate, range = c(0,75)),
#     Crude_Rate  = scales::squish(Crude_Rate, range = c(0,75))
#   )  %>%
#   mutate(Decile = factor(ntile(Crude_Rate, 10))) %>%
#   
#   ggplot(aes(x=Crude_Rate, y=Population, color=percent_rank(Crude_Rate))) + geom_jitter() +
#   scale_color_distiller(palette="RdYlBu", direction = -1, guide = 'legend')
#   scale_fill_gradientn(guide = 'legend', colours = brewer.pal(n = 9, name = 'Reds'))
#   
# 


county_laea %>%
  inner_join(TBIs, by=c("GEOID"="CountyFIPS")) %>%
  ggplot(aes(fill = percent_rank(Crude_Rate))) +
  geom_sf() +
  coord_sf(crs = 26914) +
  scale_fill_distiller(palette="RdYlBu", direction = -1, guide = 'legend',
                       labels=scales::percent, name="%tile rank of TBI deaths") +
  theme(legend.direction="horizontal",legend.position=c(0.5,0))
```

# Leaflet

```{r}
leaflet_df <- population_leaflet %>%
  left_join(by=c("GEOID"="CountyFIPS"),
            TBIs) %>%
  left_join(by=c("GEOID"="county_FIPS"),
            summarise(group_by(providers, county_FIPS), NPIs=n())
  ) %>%
  replace_na(list(NPIs=0)) %>%
  sf::st_transform(4326) %>%
  filter(!str_detect(GEOID, "72..."), !str_detect(GEOID, "02..."),
         !str_detect(GEOID, "15...")) %>%
  mutate(
    Percentile_TBI = percent_rank(Crude_Rate),
    # TBI_label = glue::glue("{NAME}\n\n{round(Crude_Rate, 1)}"),
    Ratio = NPIs*100000/estimate,
    Ratio = ifelse(Ratio==0, NA, Ratio),
    # Popup_text = paste0("<b>",NAME,"</b><br>Crude Rate: ",Crude_Rate)
    Popup_text = glue::glue("<h3>{NAME}</h3><br><b>TBI deaths:</b> {round(Crude_Rate,1)} per 100k<br>
                            <b>Percentile rank:</b> {round(Percentile_TBI*100)}<hr>
                            <b>Number of neurosurgeons:</b> {NPIs}<br>
                            <b>NSG per 100k:</b> {round(Ratio,1)}<br>")
  ) 

npi_pal <- colorBin("YlGnBu", domain=leaflet_df$Ratio, 
                    bins=c(0:2, 4, 6, Inf),
                    na.color="#C0C0C0")
tbi_pal <- colorQuantile("RdYlBu", na.color="#C0C0C0", reverse=T, 
                         domain=leaflet_df$Crude_Rate)  
  
  
leaflet_df %>%
  leaflet() %>%
  addProviderTiles("CartoDB.Positron", group="Base") %>%
  addProviderTiles("Stamen.TonerLabels", group = "Base") %>%
  
  
  # %tile rank of county's crude rate of TBI deaths
  addPolygons(
    fillColor = ~tbi_pal(Crude_Rate), 
    stroke=F, fillOpacity=0.75,
    highlight = highlightOptions(
      weight=5, color="#666", fillOpacity=0.5, bringToFront=T),
    label = ~NAME, popup = ~Popup_text,
    group = "TBI"
  ) %>%
  
  # Ratio of NPIs to 100k population
  addPolygons(
    # fillColor = ~colorNumeric("PiYG", Ratio, na.color="grey50")(Ratio), 
    fillColor = ~npi_pal(Ratio),
    stroke=F, fillOpacity=0.9,
    highlight = highlightOptions(
      weight=5, color="#666", fillOpacity=0.5, bringToFront=T),
    label = ~NAME, popup = ~Popup_text,
    group = "NPIs"
  ) %>%
  
  # population
  addPolygons(
    fillColor = ~colorNumeric("viridis", log(estimate))(log(estimate)),
    stroke = FALSE, group = "population"
  ) %>%
  
  # legends
  addLegend(pal = tbi_pal, values = ~Crude_Rate,
            opacity = 0.7, title = "%tile rank TBI deaths",
            position = "bottomright", group="TBI") %>%
  addLegend(pal = npi_pal, values = ~Ratio,
            opacity = 0.7, title = "NSG per 100k",
            position = "bottomleft", group="NPIs") %>%
  
  # Control layers
  addLayersControl(
    baseGroups = c("TBI", "NPIs", "Population"),
    options = layersControlOptions(collapsed = FALSE)
  )
```

# Find neighbors by distance

```{r, eval=F}
options(tigris_class = "sf")
TX <- counties("TX", cb=T)

function_X <- function(geo_sf) {
  
  # Counties w/o providers
  missing <- geo_sf %>%
    filter(!GEOID %in% providers$county_FIPS) %>%
    # sample_n(5) %>%
    sf::as_Spatial() %>%
    coordinates()
  
  has_providers <- geo_sf %>%
    filter(GEOID %in% providers$county_FIPS) %>%
    sf::as_Spatial() %>%
    coordinates()
  
  dist.mat <- geosphere::dist2Line(p = missing, line = has_providers)
  cbind(missing, dist.mat)
}

X <- function_X(TX)
dimnames(X)[[2]] <- c("lon0", "lat0", "distance", "lon", "lat")


providers %>%
  filter(state=="TX") %>%
  ungroup() %>% count(county_FIPS, county_name)



fortify(TX) %>%
  ggplot() +
  geom_map(aes(x=long, y=lat, map_id=id),
           map=fortify(TX),
           color="black", fill="white", size=0.25) +
  coord_quickmap()
```


```{r, eval=F}
TX <- counties("TX", cb=T)
TX$id <- 1:nrow(TX)

coords <- providers %>% 
  filter(state=="TX") %>%
  ungroup() %>% 
  select(lon, lat) %>% 
  sample_n(10) %>%
  unique() %>%
  as.matrix() 

dnearneigh(coordinates(TX), 0, 50, longlat = T) %>%
  plot(coordinates(TX))
  
dnearneigh(coordinates(TX), 0, 40, longlat = T) %>%
  # plot(coordinates(TX))
  include.self() %>%
  nb2listw()

  dnearneigh(coordinates(TX), 0, 50, longlat = TRUE)


plot(TX)
pts <- locator(5,type="p")
geosphere::dist2Line(p = SpatialPoints(pts), line = TX)

pts2 <- sp::makegrid(wrld_simpl, n = 5)
apply(gDistance(SpatialPoints(pts, proj4string=CRS(proj4string(TX))), TX,byid=TRUE),2,min)

geosphere::dist2Line


```


# Google Maps Geocode

```{r}
# ggeocode <- providers %>%
#   mutate(address = str_glue("{firstName} {lastName} neurosurgeon")) %>%
#   ungroup() %>%
#   sample_n(10) %>%
#   mutate_geocode(location = address, output = "more")
```

# Useful links

http://personal.tcu.edu/kylewalker/spatial-neighbors-in-r.html

https://gist.github.com/walkerke/6915b02ac7f0c215bc2c75a687b3d269

[Calculating distance](https://gis.stackexchange.com/questions/225102/calculate-distance-between-points-and-nearest-polygon-in-r/254310)

[Filtering with TIGRIS](https://www.r-bloggers.com/generating-metropolitan-subsets-of-census-data-with-r-and-tigris/)

