---
title: "JSR Manuscript Calculations"
author: "Hunter Ratliff, htratlif@utmb.edu"
date: "7/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=F, warning=F, message=F)
library(magrittr)
library(scales)
library(RColorBrewer)
library(ggthemes)
library(cowplot)
library(sf)       # newer, better version of sp
library(tigris)   # for shapefiles
library(sjPlot);  # for lm plots
library(qwraps2)  # gives nice wrapper to calculate mean/CI with inline R code
library(texreg)   # Pretty regression tables
library(tidyverse)
library(gt)

# settings for tigris
options(tigris_class = "sf")
options(tigris_use_cache = T) 

# functions to print stats inline
print_mean_ci <- function(x) str_glue("{print(frmtci(mean_ci(x), format = 'est (lcl - ucl)'))}")
print_mean_sd <- function(x) str_glue("{print(qwraps2::mean_sd(x, na_rm = T))}")



########################
###   READ IN DATA   ###
### ---------------- ###
# get shapefiles for US counties & states
US_counties <- tigris::counties(state = c(state.abb, "DC"), cb=T, resolution = "5m") %>%
  filter(STATEFP!="02", STATEFP!="15")
US_states <- tigris::states(cb=T, resolution = "5m") %>%
  filter(STATEFP %in% unique(US_counties$STATEFP))

# Distances for each county (from review_comment_v1.Rmd)
# distances <- read_csv("Data/County_Distances-WEIGHTED.csv")
distances <- paste0("https://raw.githubusercontent.com/HunterRatliff1/",
                    "NSG_geography/master/public_data/County_Distances-WEIGHTED.csv") %>%
  read_csv()


# Our main dataset
df_full <- paste0("https://raw.githubusercontent.com/HunterRatliff1/",
                  "NSG_geography/master/public_data/regression.csv") %>%
  read_csv() %>%
  
  select(-region, -division) %>%
  mutate(male   = male * 100,
         Over65 = Over65 *100) %>%
  mutate(Urbanization = forcats::fct_relevel(Urbanization, "Metro")) %>%
  
  # Drop old distance, add new distance
  select(-starts_with("dist_")) %>%
  inner_join(distances)

df <- df_full %>%
  filter(!is.na(Deaths)) # drop counties with missing rates

rm(distances)
```

# Methods info

```{r, echo=T, collapse=T}
## Number of neurosurgeons:
read_csv("Google_results/geo_google_raw.csv") %>%
  filter(geoState!="hi", geoState!="ak") %>%
  nrow()

## Number of trauma facilites
read_csv("POS_2017/geocoded/POS_2017_tracts.csv", 
                col_types = cols(Census.Tracts.GEOID = col_character(), 
                                 accuracy = col_double(), type = col_character())) %>%
  filter(HospType!="Long term") %>%
  filter(Trauma) %>%
  nrow()
```

# Results

Univariate descriptive statistics for each variable can be found in *Table 1*. The mean (95% CI) mortality rate among all counties was <b>`r frmtci(mean_ci(df$Crude), format = "est (lcl - ucl)")`</b> per 100,000 population (*Figure 1*). The mean (95% CI) distance to the nearest neurosurgeon was <b>`r frmtci(mean_ci(df$dist_nsg_cent), format = "est (lcl - ucl)")`</b> miles (*Figure 2*). 

```{r}
read_csv("Google_results/geo_google_raw.csv") %>%
  filter(geoState!="hi", geoState!="ak") %>%
  rename(GEOID=geoCounty) %>%
  left_join(select(df_full, GEOID, Urbanization)) %>%
  count(Urbanization) %>%
  mutate(`%` = round(n/sum(n), 4)*100)
  
  
```


```{r Table_1,results='asis'}
options(qwraps2_markup = "markdown")
df_compare_missing <- df_full %>%
  anti_join(df) %>%
  mutate(Exclude = T) %>%
  bind_rows(df) %>%
  mutate(Exclude = replace_na(Exclude, F)) %>%
  group_by(Exclude) 

tbl1_summary <- list("Distance to nearest neurosurgeon (miles)" =
                       list("Mean (95% CI)" = ~ frmtci(qwraps2::mean_ci(.data$dist_nsg_cent)),
                            "Median (IQR)"  = ~ qwraps2::median_iqr(.data$dist_nsg_cent)),
                     "Distance to nearest trauma facility (miles)" = 
                       list("Mean (95% CI)" = ~ frmtci(qwraps2::mean_ci(.data$dist_trm_cent)),
                            "Median (IQR)"  = ~ qwraps2::median_iqr(.data$dist_trm_cent)),
                     "% Male" = 
                       list("Mean (95% CI)" = ~ frmtci(qwraps2::mean_ci(.data$male)),
                            # "Mean (SD)"     = ~ qwraps2::mean_sd(.data$male, denote_sd = "paren"),
                            "Median (IQR)"  = ~ qwraps2::median_iqr(.data$male)),
                     "% 65 or older" = 
                       list("Mean (95% CI)" = ~ frmtci(qwraps2::mean_ci(.data$Over65)),
                            # "Mean (SD)"     = ~ qwraps2::mean_sd(.data$Over65, denote_sd = "paren"),
                            "Median (IQR)"  = ~ qwraps2::median_iqr(.data$Over65)),
                     "Urbanization" = 
                       list("Metro (%)"     = ~ qwraps2::n_perc0(.data$Urbanization == "Metro"),
                            "Nonmetro (%)"  = ~ qwraps2::n_perc0(.data$Urbanization == "Nonmetro"),
                            "Rural (%)"     = ~ qwraps2::n_perc0(.data$Urbanization == "Rural")),
                     "Population" =
                       list("Mean (95% CI)" = ~ frmtci(qwraps2::mean_ci(.data$StdPop), digits=0),
                            # "Mean (SD)"     = ~ qwraps2::mean_sd(.data$StdPop, digits=0, denote_sd = "paren"),
                            "Median (IQR)"  = ~ qwraps2::median_iqr(.data$StdPop, digits=0))
)

cbind(
  {df_compare_missing %>% ungroup() %>% summary_table(tbl1_summary)},
  {df_compare_missing %>% group_by(Exclude)  %>% summary_table(tbl1_summary)}
) %>% print(rtitle = "Table 1")

## Sup table 1
# df %>%
#   mutate(male   = male * 100,
#          Over65 = Over65 * 100) %>%
#   select(Crude, AgeAdj, dist_cent, male, Over65, Urbanization, num_provs) %>%
#   select(-num_provs) %>%
#   desctable::desctable(stats = list("N"            = length,
#                                     "Mean +/- SD"  = qwraps2::mean_sd,
#                                     "median (IQR)" = qwraps2::median_iqr,
#                                     "min"          = min,
#                                     "max"          = max,
#                                     "%"            = is.factor ~ percent),
#                        labels = c(Over65    =  "65 years or older (%)",
#                                   male      = "Male (%)",
#                                   dist_cent = "Distance (miles)",
#                                   Crude     = "Crude rate",
#                                   AgeAdj    = "Age adjusted rate")) %>%
#   desctable::pander.desctable()

# top_n(df, 1, wt=dist_cent) %>% str_glue_data("{NAME}, {ST} with a distance of {round(dist_cent)} miles") 
```


```{r Fig1, cache=TRUE, eval=FALSE}
########################
##   CACHED RESULTS   ##
########################
## Take care not to edit this chunk unless you absolutly must, since it takes a minute to render
##
##

Fig_rates <- US_counties %>%
  # filter(STATEFP=="48") %>%
  geo_join(df, by="GEOID") %>%
  ggplot() +

  geom_sf(data = US_states, fill=NA, color="black") +
  geom_sf(aes(fill=Crude), color=NA) +

  coord_sf(crs = 4269) + # RdYlGn
  scale_fill_distiller(palette="RdYlGn", guide = 'legend',
                       na.value = "grey50",
                       breaks = c(10,20,40,60),
                       values=scales::rescale(quantile(df$Crude)),
                       name="TBI Mortality Rate\n(per 100,000)", direction=-1) +
  # theme_dark()
  ggthemes::theme_map() +
  # labs(title = "[Fig 1] TBI Mortality Rates") +
  theme(legend.direction="horizontal")

Fig_rates # export: 700 x 450

Fig_rates + scale_fill_distiller(palette="Greys", guide = 'legend',
                       na.value = "black",
                       breaks = c(10,20,40,60),
                       values=scales::rescale(quantile(df$Crude)),
                       name="TBI Mortality Rate\n(per 100,000)", direction=1) 
```

```{r Fig2, cache=TRUE, eval=FALSE}
########################
##   CACHED RESULTS   ##
########################
## Take care not to edit this chunk unless you absolutly must, since it takes a minute to render
##
##

Fig_dist <- US_counties %>%
  select(-NAME) %>%
  # filter(STATEFP=="48") %>%
  geo_join(df_full, by="GEOID") %>%
  ggplot() +
  
  geom_sf(data = US_states, fill=NA, color="black") +
  geom_sf(aes(fill=dist_cent), color=NA) + 
  
  coord_sf(crs = 4269) +
  scale_fill_distiller(palette="Blues", guide = 'legend',
                       na.value = "grey50",
                       trans="sqrt",
                       # values=scales::rescale(quantile(df$dist_cent)),
                       name="Distance (miles)", direction=1) +
  # theme_dark()
  ggthemes::theme_map() +
  # labs(title = "[Fig 2] Distance to nearest neurosurgeon") +
  theme(legend.direction="horizontal") 

Fig_dist # export: 700 x 450

Fig_dist + scale_fill_distiller(palette="Greys", guide = 'legend',
                       na.value = "grey50",
                       trans="sqrt",
                       # values=scales::rescale(quantile(df$dist_cent)),
                       name="Distance (miles)", direction=1) 
```

## Missing TBI Rates

 

```{r, include=F}
#  tests for sup table 1

# Distance to neurosurgeon
qplot(dist_nsg_cent, Exclude, geom="boxplot", data=df_compare_missing)
qplot(dist_nsg_cent, fill=Exclude, geom="density", alpha=.5, data=df_compare_missing)
t.test(dist_nsg_cent ~ Exclude, data=df_compare_missing)

# Distance to trauma facility
qplot(dist_trm_cent, Exclude, geom="boxplot", data=df_compare_missing)
qplot(dist_trm_cent, fill=Exclude, geom="density", alpha=.5, data=df_compare_missing)
t.test(dist_trm_cent ~ Exclude, data=df_compare_missing)

# Male
qplot(male, Exclude, geom="boxplot", data=df_compare_missing)
qplot(male, fill=Exclude, geom="density", alpha=.5, data=df_compare_missing)
t.test(male ~ Exclude, data=df_compare_missing)

# Over 65
qplot(Over65, Exclude, geom="boxplot", data=df_compare_missing)
qplot(Over65, fill=Exclude, geom="density", alpha=.5, data=df_compare_missing)
t.test(Over65 ~ Exclude, data=df_compare_missing)

# Urbanization
mosaicplot(Urbanization~Exclude, data=df_compare_missing)
chisq.test(df_compare_missing$Urbanization, df_compare_missing$Exclude)

# Population
qplot(StdPop, fill=Exclude, geom="density", alpha=.5, data=df_compare_missing) + scale_x_log10()
wilcox.test(StdPop ~ Exclude, data=df_compare_missing)

## How much of the population is missing?
df_full %>%
  mutate(missing = ifelse(is.na(Deaths), "Missing", "No")) %>%
  group_by(missing) %>%
  summarise(
    num = n(),
    pop = sum(pop12)
  ) %>%
  mutate(`% missing`=num/sum(num),
         `% pop` = pop/sum(pop))
```

## Bivariate & Multivariate

First some helper functions

```{r}
make_table_2 <- function(.data, 
                         family="nb", # can be p, qp, or nb
                         divide_distance=25, 
                         return_mods=F,
                         baseVars=c("male", "Over65", "Urbanization")){
  
  # Internal function
  bivariate <- function(.data, 
                      model_type = "p", # can be p, qp, or nb
                      base_vars=baseVars,
                      key_predictors = c("dist_nsg_cent", "dist_trm_cent")) {
  
  all_preds <- c(base_vars, key_predictors)
  all_preds <- c(all_preds, paste0(all_preds, collapse = " + "))
  
  
  fit_mod <- function(x){
    formula1 <- paste("Deaths  ~ offset(log(StdPop)) + ", x) %>% as.formula()
    
    if(model_type=="p")  mod <- glm(formula1,          data=.data, family = poisson())
    if(model_type=="qp") mod <- glm(formula1,          data=.data, family = quasipoisson())
    if(model_type=="nb") mod <- MASS::glm.nb(formula1, data=.data)
    
    mod
    
  }
  
  bivar_mods <- all_preds %>%
    map(~fit_mod(.x)) 

  
  }
  
  # Internal function
  extract_mods <- function(x){
    # Determine the number of predictors
    # (used to determine if adjusted model later)
    n_predictors <- length(unlist(insight::find_predictors(x)))
    
    x %>% 
      parameters::model_parameters(exponentiate=T) %>%
      as_tibble() %>%
      select(Parameter, Coefficient, CI_low, CI_high, p) %>%
      mutate(n_predictors = n_predictors)
  }
    
  ########################
  ###   BEGIN SCRIPT   ###
  ### ---------------- ###
  cli::cli_alert_info('Using model family {switch(family, "p"="Poisson", "qp"="Quasipoisson", "nb"="Negative Binomial")}')
  cli::cli_alert_info('All distances are divided by {divide_distance}')
  
  
  mods <- .data %>%
    mutate_at(vars(starts_with("dist_")), ~.x/divide_distance) %>%
    bivariate(model_type = family)
  
  # if(family=="p") AER::dispersiontest( mods[[length(mods)]] )
  
  if(return_mods) return(mods)
  
  
  mods %>% 
  map_df(extract_mods) %>%
  mutate(adjusted = if_else(n_predictors==max(n_predictors), "Adjusted", "Bivariate")) %>%
  filter(!str_detect(Parameter, "Intercept")) %>%
  mutate(CI = str_glue("({signif(CI_low, 3)} - {signif(CI_high, 3)})"),
         Coefficient = signif(Coefficient, 3),
         p = ifelse(p<.001, "<0.001", round(p, 3))) %>%
  
  select(Parameter, Coefficient, CI, p, adjusted) %>%
  pivot_wider(names_from = adjusted, 
              names_glue = "{.value}.{adjusted}",
              values_from=-Parameter) %>%

  select(-starts_with("adjusted")) %>%
  
  gt(rowname_col = "Parameter") %>% 
  tab_spanner(
    label = "Unadjusted",
    columns = ends_with("Bivariate")
  ) %>%
  tab_spanner(
    label = "Adjusted",
    columns = ends_with("Adjusted")
  ) %>%
  
  cols_label(
    Coefficient.Bivariate = "IRR",
    Coefficient.Adjusted  = "aIRR",
    CI.Bivariate  = "95% CI",
    CI.Adjusted   = "95% CI",
    p.Bivariate   = "p value",
    p.Adjusted    = "p value"
  ) %>%
  
  tab_header(
    title = "Table 2",
    subtitle = paste0("Using a ", # insight::model_info(mods[[6]])$family
                      switch(family, "p"="Poisson", "qp"="Quasipoisson", "nb"="Negative Binomial"), 
                      " regression")
  ) %>%
  tab_footnote(
    footnote = paste0("Per ", divide_distance ," mile increase in distance"),
    locations = cells_stub(rows = contains("dist"))
  )
}




```

We also might need to settle on which unit of analysis to use. Right now, I'm presenting distance using the following

```{r, echo=T, message=T, collapse=T}
# Fit models for table 2, using specified family
make_table_2(df, family = "nb", divide_distance = 25)
base_mod <- make_table_2(df, family = "nb", divide_distance = 25, return_mods = T)[[6]]
```

```{r, echo=T, message=T, collapse=T}
make_table_2(df, family = "qp", divide_distance = 25) 
```

```{r}
# # mods %>% sjPlot::tab_model(collapse.ci = T, show.aic = T)
# 
# mods %>% 
#   map_df(extract_mods) %>%
#   mutate(adjusted = if_else(n_predictors==max(n_predictors), "Adjusted", "Bivariate")) %>%
#   filter(!str_detect(Parameter, "Intercept")) %>%
#   mutate(CI = str_glue("({signif(CI_low, 3)} - {signif(CI_high, 3)})"),
#          Coefficient = signif(Coefficient, 3),
#          p = ifelse(p<.001, "<0.001", round(p, 3))) %>%
#   
#   select(Parameter, Coefficient, CI, p, adjusted) %>%
#   pivot_wider(names_from = adjusted, 
#               names_glue = "{.value}.{adjusted}",
#               values_from=-Parameter) %>%
# 
#   select(-starts_with("adjusted")) %>%
#   
#   gt() %>% 
#   tab_spanner(
#     label = "Unadjusted",
#     columns = ends_with("Bivariate")
#   ) %>%
#   tab_spanner(
#     label = "Adjusted",
#     columns = ends_with("Adjusted")
#   ) %>%
#   
#   cols_label(
#     Coefficient.Bivariate = "MRR",
#     Coefficient.Adjusted  = "aMRR",
#     CI.Bivariate  = "95% CI",
#     CI.Adjusted   = "95% CI",
#     p.Bivariate   = "p value",
#     p.Adjusted    = "p value"
#   ) %>%
#   
#   tab_header(
#     title = "Table 2",
#     subtitle = paste0("Using a ", insight::model_info(mods[[6]])$family, " regression")
#   ) 


```

## Sensitivity

This is the formula used for our main analysis. Assure that this is the same for sensitivity analysis

```{r}
insight::find_formula(base_mod)$conditional
```

```{r}
base_mod <- MASS::glm.nb(Deaths ~ offset(log(StdPop)) + male + Over65 + Urbanization +
                           dist_nsg_cent + dist_trm_cent, 
                         data = mutate_at(df, vars(starts_with("dist_")), ~.x/25))

mod_A <- base_mod %>%
  parameters::model_parameters(exponentiate=T) %>%
      as_tibble() %>%
      select(Parameter, Coefficient, CI_low, CI_high, p) %>%
  mutate(Mod = "A")

mod_B <- mutate_at(df, vars(starts_with("dist_")), ~.x/25) %>% 
  # select(Deaths:StdPop) %>%
  mutate(Deaths2 = round(AgeAdj * StdPop / 1e5)) %>%
  update(base_mod, Deaths2~., data=.) %>%
  parameters::model_parameters(exponentiate=T) %>%
      as_tibble() %>%
      select(Parameter, Coefficient, CI_low, CI_high, p) %>%
  mutate(Mod = "B")

mod_C <- update(base_mod, .~. - dist_trm_cent)  %>% 
      parameters::model_parameters(exponentiate=T) %>%
      as_tibble() %>%
      select(Parameter, Coefficient, CI_low, CI_high, p) %>%
  mutate(Mod = "C")
# mod_C <- update(base_mod, .~. + dist_nsg_min + dist_trm_min - dist_nsg_cent - dist_trm_cent)  %>% 
#       parameters::model_parameters(exponentiate=T) %>%
#       as_tibble() %>%
#       select(Parameter, Coefficient, CI_low, CI_high, p) %>%
#   mutate(Mod = "C")

mod_D <- update(base_mod, .~. - dist_nsg_cent)  %>% 
      parameters::model_parameters(exponentiate=T) %>%
      as_tibble() %>%
      select(Parameter, Coefficient, CI_low, CI_high, p) %>%
  mutate(Mod = "D")
# mod_D <- update(base_mod, .~. + dist_nsg_min + dist_trm_min - dist_nsg_cent - dist_trm_cent, 
#                 subset = dist_nsg_min != 0)  %>% 
#       parameters::model_parameters(exponentiate=T) %>%
#       as_tibble() %>%
#       select(Parameter, Coefficient, CI_low, CI_high, p) %>%
#   mutate(Mod = "D")

bind_rows(mod_A, mod_B, mod_C, mod_D) %>%
  filter(!str_detect(Parameter, "Intercept")) %>%
  mutate(Parameter = case_when(str_detect(Parameter, "^dist_nsg") ~ "NSG",
                               str_detect(Parameter, "^dist_trm") ~ "Trauma",
                               TRUE                               ~ Parameter)) %>%
  mutate(IRR = str_glue("{signif(Coefficient, 3)} ({signif(CI_low, 3)} - {signif(CI_high, 3)})"),
         p_category = case_when(p<.001 ~ "***",
                                p<.01  ~ "**",
                                p<.05  ~ "*",
                                # TRUE   ~ as.character(round(p, 2)))) %>%
                                TRUE   ~ "")) %>%
  
  select(Mod, Parameter, IRR, p_category) %>%
  mutate(IRR = paste0(IRR, p_category)) %>% select(-p_category) %>%
  
  pivot_wider(values_from = "IRR", names_from = "Mod") %>%
  gt(rowname_col = "Parameter") %>%
  tab_header(
    title = "Table 3"
  ) 
rm(mod_A, mod_B, mod_C, mod_D)
```

# Addressing the 20% of missing counties

```{r}
rate_needed <- df_full %>%
  # anti_join(df) %>%
  filter(is.na(Deaths)) %>%
  mutate(RateNeeded = 100000*20/StdPop) 

rate_needed <- predict(base_mod, rate_needed, interval="prediction") %>%
  as_tibble() %>%
  bind_cols(rate_needed) %>%
  rename(pred_rate=value)
  # rename(pred_rate=fit, pred_rate.lwr=lwr, pred_rate.upr=upr)

rate_needed %>%
  mutate(pred_deaths = pred_rate*StdPop/100000) %>%
  .$pred_deaths %>% print_mean_sd()
  # View()
  mutate(OverPredict = pred_deaths > 20) %>%
  count(OverPredict) %>%
  mutate(`%` = n/sum(n))
```

# Other discussion stuff

```{r}
df_full %>% group_by(dist_nsg_min>0) %>% summarise(pop=sum(pop12)) %>% mutate(`%`=pop/sum(pop))
df_full %>% group_by(dist_nsg_min>0) %>% summarise(counties=n()) %>% mutate(`%`=counties/sum(counties))
```


# Other stuff

```{r}
library(tidycensus)

vars_acs <- tidycensus::load_variables(2013, "acs5") 

prop_poverty <- get_acs("county", variables = c("B17015_002"),
                   summary_var = "B17015_001",
                   year = 2013) %>%
  # Replace missing moe's with 0
  replace_na(list(moe=0, summary_moe=0)) %>%
  
  # # ## Join to names of variables
  # # left_join(vars_acs12, by=c("variable"="name")) %>% select(-concept) %>%
  # 
  # ## Make variables readable
  # mutate(variable = str_remove(variable, "B01001_")) %>%
  # mutate(variable = case_when(variable=="002" ~ "Males",
  #                             variable=="026" ~ "Females")) %>%
  # ## Find proportion males 
  # filter(variable=="Males") %>%
  mutate(poverty     = estimate/summary_est,
         poverty_moe = moe_prop(estimate, summary_est, moe, summary_moe)) %>%
  select(GEOID, poverty, poverty_moe) %>%
  
  # Filter AK, HI, and PR  &   recode two counties
  filter(!str_detect(GEOID, "^02"), 
         !str_detect(GEOID, "^15"), 
         !str_detect(GEOID, "^72")) %>%
  mutate(GEOID = recode(GEOID, "46113"="46102"))
# ignore "51515"="51019"


prop_poverty %>% select(GEOID, poverty, poverty_moe) %>% anti_join(df_full)
semi_join(df_full, prop_poverty) %>% anti_join(df_full)
df_full %>% inner_join(prop_poverty)

df %>% inner_join(prop_poverty) %>% 
  make_table_2(family = "nb", divide_distance = 25, 
               baseVars = c("male", "Over65", "Urbanization", "poverty"))
```

```{r}
library(tidycensus)
prop_ins <- get_acs("county", variables = c("B27001_002"),
                   summary_var = "B27001_001",
                   year = 2013) %>%
  # Replace missing moe's with 0
  replace_na(list(moe=0, summary_moe=0)) %>%
  
  # # ## Join to names of variables
  # # left_join(vars_acs12, by=c("variable"="name")) %>% select(-concept) %>%
  # 
  # ## Make variables readable
  # mutate(variable = str_remove(variable, "B01001_")) %>%
  # mutate(variable = case_when(variable=="002" ~ "Males",
  #                             variable=="026" ~ "Females")) %>%
  # ## Find proportion males 
  # filter(variable=="Males") %>%
  mutate(poverty     = estimate/summary_est,
         poverty_moe = moe_prop(estimate, summary_est, moe, summary_moe)) %>%
  select(GEOID, poverty, poverty_moe) %>%
  
  # Filter AK, HI, and PR  &   recode two counties
  filter(!str_detect(GEOID, "^02"), 
         !str_detect(GEOID, "^15"), 
         !str_detect(GEOID, "^72")) %>%
  mutate(GEOID = recode(GEOID, "46113"="46102"))
# ignore "51515"="51019"
```


```{r}
df_full %>%
  group_by(Urbanization) %>%
  filter(!is.na(Deaths)) %>%
  summarise(NSG = mean(dist_nsg_cent),
            Trauma = mean(dist_trm_cent))
```


# Pretty maps

## Figure 2

```{r}
Fig_dist <- US_counties %>%
  select(-NAME) %>%
  # filter(STATEFP=="48") %>%
  geo_join(df_full, by="GEOID") %>%
  ggplot() +
  
  geom_sf(data = US_states, fill=NA, color="black") +
  geom_sf(aes(fill=dist_nsg_cent), color=NA) + 
  
  coord_sf(crs = 4269) +
  scale_fill_distiller(palette="Blues", guide = 'legend',
                       na.value = "grey50",
                       trans="sqrt",
                       # values=scales::rescale(quantile(df$dist_cent)),
                       name="Distance (miles)", direction=1) +
  # theme_dark()
  ggthemes::theme_map() +
  # labs(title = "[Fig 2] Distance to nearest neurosurgeon") +
  theme(legend.direction="horizontal") 

Fig_dist # export: 700 x 450

Fig_dist + scale_fill_distiller(palette="Greys", guide = 'legend',
                       na.value = "grey50",
                       trans="sqrt",
                       # values=scales::rescale(quantile(df$dist_cent)),
                       name="Distance (miles)", direction=1) 
```


## OTHER

```{r}
POS <- read_csv("POS_2017/geocoded/POS_2017_tracts.csv", 
                col_types = cols(Census.Tracts.GEOID = col_character(), 
                                 accuracy = col_double(), type = col_character())) %>%
  filter(HospType!="Long term") %>%
  filter(!state %in% c("HI", "AK", "GU", "PR")) %>%
  st_as_sf(coords = c("long", "lat"), crs=4269)

provs <- read_csv("Google_results/geo_google_raw.csv") %>%
  filter(geoState!="hi", geoState!="ak") %>%
  st_as_sf(coords = c("lon", "lat"), crs=4269)



# settings for tigris
options(tigris_class = "sf")
options(tigris_use_cache = T) 

# ## Counties  c(state.abb, "DC")
# c("TX", "MO") %>%
#   map(~tigris::tracts(state = .x, cb=T) ) %>%
#   rbind_tigris()
# 
# 
# TX_tracts <- tigris::tracts(state = "TX", cb=T) 
# MO_tracts <- tigris::tracts(state = "MO", cb=T) 
# 
# rbind(TX_tracts, MO_tracts) %>%
#   filter(STATEFP!="02", STATEFP!="15") %>%
#   select(GEOID) %>% plot()

# filter(POS, Trauma) %>%
#   count(Census.Tracts.GEOID) %>%
#   st_drop_geometry() %>%
#   geo_join(US_tracts, ., by_sp="GEOID", by_df="Census.Tracts.GEOID")


# pts <- filter(POS, Trauma) 
# 
# 
# hex_polygons <- pts %>%
#   as_Spatial() %>% 
#   sp::spsample(type = "hexagonal", n=30000) %>%
#   sp::HexPoints2SpatialPolygons() %>%
#   st_as_sf(crs = 4269) %>%
#   st_intersection(US_states)
# 
# hex_polygons$count <- lengths(st_intersects(hex_polygons, pts))
# 
# hex_polygons %>%
#   filter(count>0) %>%
#   ggplot() +
#   geom_sf(aes(fill = count)) +
#   scale_fill_viridis_c(option = "magma", "# Trauma Facilities") +
#   theme_void()

US_counties %>% 
  select(GEOID) %>%
  geo_join(df_full, by="GEOID") %>%
  ggplot() +
  geom_sf(data = US_states, fill=NA, color="black") +
  geom_sf(aes(fill=Urbanization), color=NA) +
  coord_sf(crs = 4269) +
  ggthemes::theme_map() +
  scale_fill_brewer(direction = -1, palette = "greens") +
  geom_sf(data=filter(POS, Trauma), alpha=.25)

filter(POS, Trauma)  %>%
  # count(state)
  ggplot() +
  
  geom_sf(data = US_counties) +
  # stat_bin2d(data=x, aes(long, lat), binwidth = .5) +
  geom_sf()

ggplot() + stat_bin2d(data=x, aes(long, lat), binwidth = .5)
```

