---
title: "JSR Manuscript Calculations"
author: "Hunter Ratliff, htratlif@utmb.edu"
date: "7/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=F, warning=F, message=F)
library(magrittr)
library(scales)
library(RColorBrewer)
library(ggthemes)
library(cowplot)
library(sf)       # newer, better version of sp
library(tigris)   # for shapefiles
library(sjPlot);  # for lm plots
library(qwraps2)  # gives nice wrapper to calculate mean/CI with inline R code
library(texreg)   # Pretty regression tables
library(tidyverse)
library(gt)

# settings for tigris
options(tigris_class = "sf")
options(tigris_use_cache = T) 

# functions to print stats inline
print_mean_ci <- function(x) str_glue("{print(frmtci(mean_ci(x), format = 'est (lcl - ucl)'))}")
print_mean_sd <- function(x) str_glue("{print(qwraps2::mean_sd(x, na_rm = T))}")



########################
###   READ IN DATA   ###
### ---------------- ###
# get shapefiles for US counties & states
US_counties <- tigris::counties(state = c(state.abb, "DC"), cb=T, resolution = "5m") %>%
  filter(STATEFP!="02", STATEFP!="15")
US_states <- tigris::states(cb=T, resolution = "5m") %>%
  filter(STATEFP %in% unique(US_counties$STATEFP))

# Distances for each county (from review_comment_v1.Rmd)
# distances <- read_csv("Data/County_Distances-WEIGHTED.csv")
distances <- paste0("https://raw.githubusercontent.com/HunterRatliff1/",
                    "NSG_geography/master/public_data/County_Distances-WEIGHTED.csv") %>%
  read_csv()


# Our main dataset
df_full <- "https://raw.githubusercontent.com/HunterRatliff1/NSG_geography/master/public_data/regression.csv" %>%
  read_csv() %>%
  
  select(-region, -division) %>%
  mutate(male   = male * 100,
         Over65 = Over65 *100) %>%
  mutate(Urbanization = forcats::fct_relevel(Urbanization, "Metro")) %>%
  
  # Drop old distance, add new distance
  select(-starts_with("dist_")) %>%
  inner_join(distances)

df <- df_full %>%
  filter(!is.na(Deaths)) # drop counties with missing rates

rm(distances)
```

# Methods info

```{r, echo=T, collapse=T}
## Number of neurosurgeons:
read_csv("Google_results/geo_google_raw.csv") %>%
  filter(geoState!="hi", geoState!="ak") %>%
  nrow()

## Number of trauma facilites
read_csv("POS_2017/geocoded/POS_2017_tracts.csv", 
                col_types = cols(Census.Tracts.GEOID = col_character(), 
                                 accuracy = col_double(), type = col_character())) %>%
  filter(HospType!="Long term") %>%
  filter(Trauma) %>%
  nrow()
```

# Results

Univariate descriptive statistics for each variable can be found in *Table 1*. The mean (95% CI) mortality rate among all counties was <b>`r frmtci(mean_ci(df$Crude), format = "est (lcl - ucl)")`</b> per 100,000 population (*Figure 1*). The mean (95% CI) distance to the nearest neurosurgeon was <b>`r frmtci(mean_ci(df$dist_nsg_cent), format = "est (lcl - ucl)")`</b> miles (*Figure 2*). 

```{r Table_1,results='asis'}
options(qwraps2_markup = "markdown")
df_compare_missing <- df_full %>%
  anti_join(df) %>%
  mutate(Exclude = T) %>%
  bind_rows(df) %>%
  mutate(Exclude = replace_na(Exclude, F)) %>%
  group_by(Exclude) 

tbl1_summary <- list("Distance to nearest neurosurgeon (miles)" =
                       list("Mean (95% CI)" = ~ frmtci(qwraps2::mean_ci(.data$dist_nsg_cent)),
                            "Median (IQR)"  = ~ qwraps2::median_iqr(.data$dist_nsg_cent)),
                     "Distance to nearest trauma facility (miles)" = 
                       list("Mean (95% CI)" = ~ frmtci(qwraps2::mean_ci(.data$dist_trm_cent)),
                            "Median (IQR)"  = ~ qwraps2::median_iqr(.data$dist_trm_cent)),
                     "% Male" = 
                       list("Mean (95% CI)" = ~ frmtci(qwraps2::mean_ci(.data$male)),
                            # "Mean (SD)"     = ~ qwraps2::mean_sd(.data$male, denote_sd = "paren"),
                            "Median (IQR)"  = ~ qwraps2::median_iqr(.data$male)),
                     "% 65 or older" = 
                       list("Mean (95% CI)" = ~ frmtci(qwraps2::mean_ci(.data$Over65)),
                            # "Mean (SD)"     = ~ qwraps2::mean_sd(.data$Over65, denote_sd = "paren"),
                            "Median (IQR)"  = ~ qwraps2::median_iqr(.data$Over65)),
                     "Urbanization" = 
                       list("Metro (%)"     = ~ qwraps2::n_perc0(.data$Urbanization == "Metro"),
                            "Nonmetro (%)"  = ~ qwraps2::n_perc0(.data$Urbanization == "Nonmetro"),
                            "Rural (%)"     = ~ qwraps2::n_perc0(.data$Urbanization == "Rural")),
                     "Population" =
                       list("Mean (95% CI)" = ~ frmtci(qwraps2::mean_ci(.data$StdPop), digits=0),
                            # "Mean (SD)"     = ~ qwraps2::mean_sd(.data$StdPop, digits=0, denote_sd = "paren"),
                            "Median (IQR)"  = ~ qwraps2::median_iqr(.data$StdPop, digits=0))
)

cbind(
  {df_compare_missing %>% ungroup() %>% summary_table(tbl1_summary)},
  {df_compare_missing %>% group_by(Exclude)  %>% summary_table(tbl1_summary)}
) %>% print(rtitle = "Table 1")

## Sup table 1
# df %>%
#   mutate(male   = male * 100,
#          Over65 = Over65 * 100) %>%
#   select(Crude, AgeAdj, dist_cent, male, Over65, Urbanization, num_provs) %>%
#   select(-num_provs) %>%
#   desctable::desctable(stats = list("N"            = length,
#                                     "Mean +/- SD"  = qwraps2::mean_sd,
#                                     "median (IQR)" = qwraps2::median_iqr,
#                                     "min"          = min,
#                                     "max"          = max,
#                                     "%"            = is.factor ~ percent),
#                        labels = c(Over65    =  "65 years or older (%)",
#                                   male      = "Male (%)",
#                                   dist_cent = "Distance (miles)",
#                                   Crude     = "Crude rate",
#                                   AgeAdj    = "Age adjusted rate")) %>%
#   desctable::pander.desctable()

# top_n(df, 1, wt=dist_cent) %>% str_glue_data("{NAME}, {ST} with a distance of {round(dist_cent)} miles") 
```


```{r Fig1, cache=TRUE, eval=FALSE}
########################
##   CACHED RESULTS   ##
########################
## Take care not to edit this chunk unless you absolutly must, since it takes a minute to render
##
##

Fig_rates <- US_counties %>%
  # filter(STATEFP=="48") %>%
  geo_join(df, by="GEOID") %>%
  ggplot() +

  geom_sf(data = US_states, fill=NA, color="black") +
  geom_sf(aes(fill=Crude), color=NA) +

  coord_sf(crs = 4269) + # RdYlGn
  scale_fill_distiller(palette="RdYlGn", guide = 'legend',
                       na.value = "grey50",
                       breaks = c(10,20,40,60),
                       values=scales::rescale(quantile(df$Crude)),
                       name="TBI Mortality Rate\n(per 100,000)", direction=-1) +
  # theme_dark()
  ggthemes::theme_map() +
  # labs(title = "[Fig 1] TBI Mortality Rates") +
  theme(legend.direction="horizontal")

Fig_rates # export: 700 x 450

Fig_rates + scale_fill_distiller(palette="Greys", guide = 'legend',
                       na.value = "black",
                       breaks = c(10,20,40,60),
                       values=scales::rescale(quantile(df$Crude)),
                       name="TBI Mortality Rate\n(per 100,000)", direction=1) 
```

```{r Fig2, cache=TRUE, eval=FALSE}
########################
##   CACHED RESULTS   ##
########################
## Take care not to edit this chunk unless you absolutly must, since it takes a minute to render
##
##

Fig_dist <- US_counties %>%
  select(-NAME) %>%
  # filter(STATEFP=="48") %>%
  geo_join(df_full, by="GEOID") %>%
  ggplot() +
  
  geom_sf(data = US_states, fill=NA, color="black") +
  geom_sf(aes(fill=dist_cent), color=NA) + 
  
  coord_sf(crs = 4269) +
  scale_fill_distiller(palette="Blues", guide = 'legend',
                       na.value = "grey50",
                       trans="sqrt",
                       # values=scales::rescale(quantile(df$dist_cent)),
                       name="Distance (miles)", direction=1) +
  # theme_dark()
  ggthemes::theme_map() +
  # labs(title = "[Fig 2] Distance to nearest neurosurgeon") +
  theme(legend.direction="horizontal") 

Fig_dist # export: 700 x 450

Fig_dist + scale_fill_distiller(palette="Greys", guide = 'legend',
                       na.value = "grey50",
                       trans="sqrt",
                       # values=scales::rescale(quantile(df$dist_cent)),
                       name="Distance (miles)", direction=1) 
```

## Missing TBI Rates

 

```{r, include=F}
#  tests for sup table 1

# Distance to neurosurgeon
qplot(dist_nsg_cent, Exclude, geom="boxplot", data=df_compare_missing)
qplot(dist_nsg_cent, fill=Exclude, geom="density", alpha=.5, data=df_compare_missing)
t.test(dist_nsg_cent ~ Exclude, data=df_compare_missing)

# Distance to trauma facility
qplot(dist_trm_cent, Exclude, geom="boxplot", data=df_compare_missing)
qplot(dist_trm_cent, fill=Exclude, geom="density", alpha=.5, data=df_compare_missing)
t.test(dist_trm_cent ~ Exclude, data=df_compare_missing)

# Male
qplot(male, Exclude, geom="boxplot", data=df_compare_missing)
qplot(male, fill=Exclude, geom="density", alpha=.5, data=df_compare_missing)
t.test(male ~ Exclude, data=df_compare_missing)

# Over 65
qplot(Over65, Exclude, geom="boxplot", data=df_compare_missing)
qplot(Over65, fill=Exclude, geom="density", alpha=.5, data=df_compare_missing)
t.test(Over65 ~ Exclude, data=df_compare_missing)

# Urbanization
mosaicplot(Urbanization~Exclude, data=df_compare_missing)
chisq.test(df_compare_missing$Urbanization, df_compare_missing$Exclude)

# Population
qplot(StdPop, fill=Exclude, geom="density", alpha=.5, data=df_compare_missing) + scale_x_log10()
wilcox.test(StdPop ~ Exclude, data=df_compare_missing)

## How much of the population is missing?
df_full %>%
  mutate(missing = ifelse(is.na(Deaths), "Missing", "No")) %>%
  group_by(missing) %>%
  summarise(
    num = n(),
    pop = sum(pop12)
  ) %>%
  mutate(`% missing`=num/sum(num),
         `% pop` = pop/sum(pop))
```

# Bivariate

First some helper functions

```{r}
make_table_2 <- function(.data, 
                         family="nb", # can be p, qp, or nb
                         divide_distance=25, 
                         return_mods=F){
  
  # Internal function
  bivariate <- function(.data, 
                      model_type = "p", # can be p, qp, or nb
                      base_vars=c("male", "Over65", "Urbanization"),
                      key_predictors = c("dist_nsg_cent", "dist_trm_cent")) {
  
  all_preds <- c(base_vars, key_predictors)
  all_preds <- c(all_preds, paste0(all_preds, collapse = " + "))
  
  
  fit_mod <- function(x){
    formula1 <- paste("Deaths  ~ offset(log(StdPop)) + ", x) %>% as.formula()
    
    if(model_type=="p")  mod <- glm(formula1,          data=.data, family = poisson())
    if(model_type=="qp") mod <- glm(formula1,          data=.data, family = quasipoisson())
    if(model_type=="nb") mod <- MASS::glm.nb(formula1, data=.data)
    
    mod
    
  }
  
  bivar_mods <- all_preds %>%
    map(~fit_mod(.x)) 

  
  }
  
  # Internal function
  extract_mods <- function(x){
    # Determine the number of predictors
    # (used to determine if adjusted model later)
    n_predictors <- length(unlist(insight::find_predictors(x)))
    
    x %>% 
      parameters::model_parameters(exponentiate=T) %>%
      as_tibble() %>%
      select(Parameter, Coefficient, CI_low, CI_high, p) %>%
      mutate(n_predictors = n_predictors)
  }
    
  ########################
  ###   BEGIN SCRIPT   ###
  ### ---------------- ###
  cli::cli_alert_info('Using model family {switch(family, "p"="Poisson", "qp"="Quasipoisson", "nb"="Negative Binomial")}')
  cli::cli_alert_info('All distances are divided by {divide_distance}')
  
  
  mods <- .data %>%
    mutate_at(vars(starts_with("dist_")), ~.x/divide_distance) %>%
    bivariate(model_type = family)
  
  # if(family=="p") AER::dispersiontest( mods[[length(mods)]] )
  
  if(return_mods) return(mods)
  
  
  mods %>% 
  map_df(extract_mods) %>%
  mutate(adjusted = if_else(n_predictors==max(n_predictors), "Adjusted", "Bivariate")) %>%
  filter(!str_detect(Parameter, "Intercept")) %>%
  mutate(CI = str_glue("({signif(CI_low, 3)} - {signif(CI_high, 3)})"),
         Coefficient = signif(Coefficient, 3),
         p = ifelse(p<.001, "<0.001", round(p, 3))) %>%
  
  select(Parameter, Coefficient, CI, p, adjusted) %>%
  pivot_wider(names_from = adjusted, 
              names_glue = "{.value}.{adjusted}",
              values_from=-Parameter) %>%

  select(-starts_with("adjusted")) %>%
  
  gt(rowname_col = "Parameter") %>% 
  tab_spanner(
    label = "Unadjusted",
    columns = ends_with("Bivariate")
  ) %>%
  tab_spanner(
    label = "Adjusted",
    columns = ends_with("Adjusted")
  ) %>%
  
  cols_label(
    Coefficient.Bivariate = "MRR",
    Coefficient.Adjusted  = "aMRR",
    CI.Bivariate  = "95% CI",
    CI.Adjusted   = "95% CI",
    p.Bivariate   = "p value",
    p.Adjusted    = "p value"
  ) %>%
  
  tab_header(
    title = "Table 2",
    subtitle = paste0("Using a ", # insight::model_info(mods[[6]])$family
                      switch(family, "p"="Poisson", "qp"="Quasipoisson", "nb"="Negative Binomial"), 
                      " regression")
  ) %>%
  tab_footnote(
    footnote = paste0("Per ", divide_distance ," mile increase in distance"),
    locations = cells_stub(rows = contains("dist"))
  )
}




```

We also might need to settle on which unit of analysis to use. Right now, I'm presenting distance using the following

```{r, echo=T, message=T}
# Fit models for table 2, using specified family
make_table_2(df, family = "nb", divide_distance = 25)
```

```{r, echo=T, message=T}

make_table_2(df, family = "qp", divide_distance = 25) 
```

```{r}
# # mods %>% sjPlot::tab_model(collapse.ci = T, show.aic = T)
# 
# mods %>% 
#   map_df(extract_mods) %>%
#   mutate(adjusted = if_else(n_predictors==max(n_predictors), "Adjusted", "Bivariate")) %>%
#   filter(!str_detect(Parameter, "Intercept")) %>%
#   mutate(CI = str_glue("({signif(CI_low, 3)} - {signif(CI_high, 3)})"),
#          Coefficient = signif(Coefficient, 3),
#          p = ifelse(p<.001, "<0.001", round(p, 3))) %>%
#   
#   select(Parameter, Coefficient, CI, p, adjusted) %>%
#   pivot_wider(names_from = adjusted, 
#               names_glue = "{.value}.{adjusted}",
#               values_from=-Parameter) %>%
# 
#   select(-starts_with("adjusted")) %>%
#   
#   gt() %>% 
#   tab_spanner(
#     label = "Unadjusted",
#     columns = ends_with("Bivariate")
#   ) %>%
#   tab_spanner(
#     label = "Adjusted",
#     columns = ends_with("Adjusted")
#   ) %>%
#   
#   cols_label(
#     Coefficient.Bivariate = "MRR",
#     Coefficient.Adjusted  = "aMRR",
#     CI.Bivariate  = "95% CI",
#     CI.Adjusted   = "95% CI",
#     p.Bivariate   = "p value",
#     p.Adjusted    = "p value"
#   ) %>%
#   
#   tab_header(
#     title = "Table 2",
#     subtitle = paste0("Using a ", insight::model_info(mods[[6]])$family, " regression")
#   ) 


```



