---
title: "Poster / Abstract"
author: "Hunter Ratliff"
date: "2/13/2020"
output:
  html_document:
    code_folding: hide
    df_print: paged
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=F, warning=F, message=F)
library(magrittr)
library(scales)
library(RColorBrewer)
library(ggthemes)
library(cowplot)
library(sf)       # newer, better version of sp
library(tigris)   # for shapefiles
library(sjPlot);  # for lm plots
library(qwraps2)  # gives nice wrapper to calculate mean/CI with inline R code
library(texreg)   # Pretty regression tables
library(tidyverse)

# settings for tigris
options(tigris_class = "sf")
options(tigris_use_cache = T) 



# get shapefiles for US counties & states
US_counties <- tigris::counties(state = c(state.abb, "DC"), cb=T, resolution = "5m") %>%
  filter(STATEFP!="02", STATEFP!="15")
US_states <- tigris::states(cb=T, resolution = "5m") %>%
  filter(STATEFP %in% unique(US_counties$STATEFP))



### Run this line to get the data
df_full <- read_csv("https://raw.githubusercontent.com/HunterRatliff1/NSG_geography/master/public_data/regression.csv") %>%
  mutate(region   = factor(region),
         division = factor(division)) %>%
  mutate(male   = male * 100,
         Over65 = Over65 *100) %>%
  
  mutate(region       = forcats::fct_relevel(region, "NORTHEAST"),
         division     = forcats::fct_relevel(division, "New England"),
         Urbanization = forcats::fct_relevel(Urbanization, "Metro"))
  




df <- df_full %>%
  ## Outliers
  # filter(!GEOID %in% c("38053","20055","30085","12119","30021")) %>%
  filter(!is.na(Deaths)) # drop counties with missing rates


# functions to print stats inline
print_mean_ci <- function(x) str_glue("{print(qwraps2::mean_ci(x))}")
print_mean_sd <- function(x) str_glue("{print(qwraps2::mean_sd(x, na_rm = T))}")
```




# Results

Univariate descriptive statistics for each variable can be found in **Table 1**. The mean (95% CI) mortality rate among all counties was `r frmtci(mean_ci(df$Crude), format = "est (lcl - ucl)")` per 100,000 population (**Figure 1**). The mean (95% CI) distance to the nearest neurosurgeon was `r frmtci(mean_ci(df$dist_cent), format = "est (lcl - ucl)")` miles (**Figure 2**). 

```{r Table_1,results='asis'}
options(qwraps2_markup = "markdown")
df_compare_missing <- df_full %>%
  anti_join(df) %>%
  mutate(Exclude = T) %>%
  bind_rows(df) %>%
  mutate(Exclude = replace_na(Exclude, F)) %>%
  group_by(Exclude) 

tbl1_summary <- list("Distance (miles)" =
                       list("Mean (95% CI)" = ~ frmtci(qwraps2::mean_ci(.data$dist_cent)),
                            # "Mean (SD)"     = ~ qwraps2::mean_sd(.data$dist_cent, denote_sd = "paren"),
                            "Median (IQR)"  = ~ qwraps2::median_iqr(.data$dist_cent)),
                     "% Male" = 
                       list("Mean (95% CI)" = ~ frmtci(qwraps2::mean_ci(.data$male)),
                            # "Mean (SD)"     = ~ qwraps2::mean_sd(.data$male, denote_sd = "paren"),
                            "Median (IQR)"  = ~ qwraps2::median_iqr(.data$male)),
                     "% 65 or older" = 
                       list("Mean (95% CI)" = ~ frmtci(qwraps2::mean_ci(.data$Over65)),
                            # "Mean (SD)"     = ~ qwraps2::mean_sd(.data$Over65, denote_sd = "paren"),
                            "Median (IQR)"  = ~ qwraps2::median_iqr(.data$Over65)),
                     "Urbanization" = 
                       list("Metro (%)"     = ~ qwraps2::n_perc0(.data$Urbanization == "Metro"),
                            "Nonmetro (%)"  = ~ qwraps2::n_perc0(.data$Urbanization == "Nonmetro"),
                            "Rural (%)"     = ~ qwraps2::n_perc0(.data$Urbanization == "Rural")),
                     "Population" =
                       list("Mean (95% CI)" = ~ frmtci(qwraps2::mean_ci(.data$StdPop), digits=0),
                            # "Mean (SD)"     = ~ qwraps2::mean_sd(.data$StdPop, digits=0, denote_sd = "paren"),
                            "Median (IQR)"  = ~ qwraps2::median_iqr(.data$StdPop, digits=0))
)

cbind(
  {df_compare_missing %>% ungroup() %>% summary_table(tbl1_summary)},
  {df_compare_missing %>% group_by(Exclude)  %>% summary_table(tbl1_summary)}
) %>% print(rtitle = "Table 1")

## Sup table 1
# df %>%
#   mutate(male   = male * 100,
#          Over65 = Over65 * 100) %>%
#   select(Crude, AgeAdj, dist_cent, male, Over65, Urbanization, num_provs) %>%
#   select(-num_provs) %>%
#   desctable::desctable(stats = list("N"            = length,
#                                     "Mean +/- SD"  = qwraps2::mean_sd,
#                                     "median (IQR)" = qwraps2::median_iqr,
#                                     "min"          = min,
#                                     "max"          = max,
#                                     "%"            = is.factor ~ percent),
#                        labels = c(Over65    =  "65 years or older (%)",
#                                   male      = "Male (%)",
#                                   dist_cent = "Distance (miles)",
#                                   Crude     = "Crude rate",
#                                   AgeAdj    = "Age adjusted rate")) %>%
#   desctable::pander.desctable()

# top_n(df, 1, wt=dist_cent) %>% str_glue_data("{NAME}, {ST} with a distance of {round(dist_cent)} miles") 
```


```{r Fig1, cache=TRUE}
########################
##   CACHED RESULTS   ##
########################
## Take care not to edit this chunk unless you absolutly must, since it takes a minute to render
##
##

Fig_rates <- US_counties %>%
  # filter(STATEFP=="48") %>%
  geo_join(df, by="GEOID") %>%
  ggplot() +

  geom_sf(data = US_states, fill=NA, color="black") +
  geom_sf(aes(fill=Crude), color=NA) +

  coord_sf(crs = 4269) + # RdYlGn
  scale_fill_distiller(palette="RdYlGn", guide = 'legend',
                       na.value = "grey50",
                       breaks = c(10,20,40,60),
                       values=scales::rescale(quantile(df$Crude)),
                       name="TBI Mortality Rate\n(per 100,000)", direction=-1) +
  # theme_dark()
  ggthemes::theme_map() +
  # labs(title = "[Fig 1] TBI Mortality Rates") +
  theme(legend.direction="horizontal")

Fig_rates # export: 700 x 450

Fig_rates + scale_fill_distiller(palette="Greys", guide = 'legend',
                       na.value = "black",
                       breaks = c(10,20,40,60),
                       values=scales::rescale(quantile(df$Crude)),
                       name="TBI Mortality Rate\n(per 100,000)", direction=1) 
```

```{r Fig2, cache=TRUE}
########################
##   CACHED RESULTS   ##
########################
## Take care not to edit this chunk unless you absolutly must, since it takes a minute to render
##
##

Fig_dist <- US_counties %>%
  select(-NAME) %>%
  # filter(STATEFP=="48") %>%
  geo_join(df_full, by="GEOID") %>%
  ggplot() +
  
  geom_sf(data = US_states, fill=NA, color="black") +
  geom_sf(aes(fill=dist_cent), color=NA) + 
  
  coord_sf(crs = 4269) +
  scale_fill_distiller(palette="Blues", guide = 'legend',
                       na.value = "grey50",
                       trans="sqrt",
                       # values=scales::rescale(quantile(df$dist_cent)),
                       name="Distance (miles)", direction=1) +
  # theme_dark()
  ggthemes::theme_map() +
  # labs(title = "[Fig 2] Distance to nearest neurosurgeon") +
  theme(legend.direction="horizontal") 

Fig_dist # export: 700 x 450

Fig_dist + scale_fill_distiller(palette="Greys", guide = 'legend',
                       na.value = "grey50",
                       trans="sqrt",
                       # values=scales::rescale(quantile(df$dist_cent)),
                       name="Distance (miles)", direction=1) 
```



We geolocated `r nrow(count(read_csv("Google_results/geo_google_raw.csv"), npi))` neurosurgeons 

## Missing TBI Rates



Among the `r nrow(df_full)` counties in the continental US, `r nrow(df_full)-nrow(df)` did not have TBI mortality rates reported because they had 20 or fewer TBI deaths. When compared with counties included in our analysis, the counties with missing TBI mortality rates tended to have a greater proportion of their population who were male (50.8% vs 49.7%; p < 0.001) or 65 years or older (18.8% vs 15.2%; p < 0.001), tended to be farther from the nearest neurosurgeon (60.0 vs 30.4 miles; p < 0.001), and to be less urban (**TABLE 1**). 

Counties with missing rates also tended to have smaller populations (mean $\pm$ SD: `r frmt(mean_sd(subset(df_compare_missing, Exclude)$StdPop), digits = 0)`) than counties without missing data (`r frmt(mean_sd(subset(df_compare_missing, !Exclude)$StdPop), digits = 0)`; p<0.001), and all together counties with missing rates only accounted for 1.67% of the US population. 

```{r, include=F}
## These are the tests for Table 1

qplot(dist_cent, Exclude, geom="boxplot", data=df_compare_missing)
qplot(dist_cent, fill=Exclude, geom="density", alpha=.5, data=df_compare_missing)
t.test(dist_cent ~ Exclude, data=df_compare_missing)

qplot(StdPop, fill=Exclude, geom="density", alpha=.5, data=df_compare_missing) + scale_x_log10()
wilcox.test(StdPop ~ Exclude, data=df_compare_missing)

mosaicplot(Urbanization~Exclude, data=df_compare_missing)
chisq.test(df_compare_missing$Urbanization, df_compare_missing$Exclude)

qplot(male, Exclude, geom="boxplot", data=df_compare_missing)
qplot(male, fill=Exclude, geom="density", alpha=.5, data=df_compare_missing)
t.test(male ~ Exclude, data=df_compare_missing)

qplot(Over65, Exclude, geom="boxplot", data=df_compare_missing)
qplot(Over65, fill=Exclude, geom="density", alpha=.5, data=df_compare_missing)
t.test(Over65 ~ Exclude, data=df_compare_missing)

## How much of the population is missing?
df_full %>%
  mutate(missing = ifelse(is.na(Deaths), "Missing", "No")) %>%
  group_by(missing) %>%
  summarise(
    num = n(),
    pop = sum(pop12)
  ) %>%
  mutate(`% missing`=num/sum(num),
         `% pop` = pop/sum(pop))
```






```{r}
## These are the hypothetical rates needed in order for the data to show up
df_full %>%
  mutate(missing = is.na(Deaths)) %>%
  filter(missing) %>%
  group_by(GEOID, NAME, ST) %>%
  summarise(RateNeeded = 100000*20/StdPop) %>%
  summary()
```

# Mortality Rates (bi + multi-variate)

Crude mortality rates were the lowest in the `r nrow(subset(df, Urbanization=="Metro"))` metropolitan counties with a mean rate (95% CI) of `r frmtci(mean_ci(subset(df, Urbanization=="Metro")$Crude), format = "est (lcl - ucl)")`, followed by the `r nrow(subset(df, Urbanization=="Nonmetro"))` non-metropolitan counties with a rate of `r frmtci(mean_ci(subset(df, Urbanization=="Nonmetro")$Crude), format = "est (lcl - ucl)")`. The `r nrow(subset(df, Urbanization=="Rural"))` rural counties had the highest rate at `r frmtci(mean_ci(subset(df, Urbanization=="Rural")$Crude), format = "est (lcl - ucl)")`. 

```{r, include=F}
urban_anova <- aov(Crude~Urbanization, data=df)
car::Anova(urban_anova, type="III")

# homogeneity of variance :(
bartlett.test(Crude~Urbanization, data=df)
car::leveneTest(Crude~Urbanization, data=df)


           
oneway.test(Crude~Urbanization, data=df,
            var.equal=FALSE)
```





```{r, results = 'asis', echo = FALSE}


base_fit  <- lm(Crude  ~ dist_cent + male + Over65 + Urbanization, 
                data=mutate_at(df, vars(starts_with("dist_")), ~.x/10))

htmlreg(ci.force=T, doctype=F, list(
  lm(Crude~dist_cent, data=mutate_at(df, vars(starts_with("dist_")), ~.x/10)),
  lm(Crude~male, data=df),
  lm(Crude~Over65, data=df),
  lm(Crude~Urbanization, data=df),
 base_fit
))

htmlreg(doctype=F, list(
  lm(Crude~dist_cent, data=mutate_at(df, vars(starts_with("dist_")), ~.x/10)),
  lm(Crude~male, data=df),
  lm(Crude~Over65, data=df),
  lm(Crude~Urbanization, data=df),
 base_fit
))

```








# Sensitivity

Sens1 uses the minimum distance, but is zero inflated. Sens 2 limits the analysis to only counties without NSG

```{r, results = 'asis', echo = FALSE}
htmlreg(ci.force=T, doctype=F, 
        custom.model.names=c("Base", "Age Adjusted", "Sens 1", "Sens 2"),
        list(
          base_fit,
          update(base_fit, AgeAdj~.),
          update(base_fit, .~. + dist_min - dist_cent),
          update(base_fit, .~. + dist_min - dist_cent, subset = dist_min!=0)
))

htmlreg(doctype=F, 
        custom.model.names=c("Base", "Age Adjusted", "Sens 1", "Sens 2"),
        list(
          base_fit,
          update(base_fit, AgeAdj~.),
          update(base_fit, .~. + dist_min - dist_cent),
          update(base_fit, .~. + dist_min - dist_cent, subset = dist_min!=0)
))
```















# Other maps

```{r Fig3}
Fig_urban <- read_csv("Google_results/geo_google_raw.csv") %>%
  filter(geoState!="hi", geoState!="ak") %>%
  st_as_sf(coords = c("lon", "lat"), crs=4269) %>%
  ggplot() + 
  
  geom_sf(data = US_states, fill=NA, color="black") +
  geom_sf(data = geo_join(select(US_counties, -NAME), df_full, by="GEOID"), 
          aes(fill=Urbanization), color=NA) +
  geom_sf(alpha=0.25) +
  
  
  coord_sf(crs = 4269) +
  ggthemes::theme_map() +
  scale_fill_brewer(direction = -1, palette = "greens") +
  # labs(title = "[Fig 3] Urbanization Level") +
  theme(legend.direction="horizontal") 
Fig_urban  # export: 700 x 450

Fig_urban + scale_fill_brewer(direction = -1, palette = "Greys") 
```

# imputed rates

```{r}
TBIs_org <- read_csv("Data/TBI_Deaths.csv") %>%
  # Correct Shannon, SD to it's new name
  mutate(CountyFIPS = ifelse(CountyFIPS=="46113", "46102", CountyFIPS),
         County     = ifelse(CountyFIPS=="46102", "OGLALA LAKOTA", County)) %>%
  
  ## logical indicating if deaths was originally missing
  mutate(imputed = is.na(Deaths))

TBI_Overall_state <- read_csv("TBI_data/State/TBI_Overall_state.csv") %>%
  select(ST:Deaths_ST)


TBI_imputed <- TBIs_org %>%
  # filter(ST=="MA") %>%
  
  ## For each state, find the number of deaths accounted for, and 
  ## total population of those counties with rates
  group_by(ST, imputed) %>%
  summarise(Deaths = sum(Deaths, na.rm = T),
            Pop    = sum(Population, na.rm=T)) %>%
  left_join(TBI_Overall_state) %>%
  
  
  ## Limiting to counties with existing rates, find the
  ## number of deaths and population unaccounted for
  filter(!imputed) %>%
  mutate(Pop_miss    = StdPop_ST - Pop,
         Deaths_miss = Deaths_ST - Deaths) %>%
  
  
  ## Determine the hypothetical mortality rate in
  ## counties with missing data. Join to original
  ## data.frame
  mutate(rate_miss = Deaths_miss/Pop_miss) %>%  # This is the raw rate (not the rate per 100,000)
  select(ST, rate_miss, starts_with("n_"), Deaths_miss) %>%
  left_join(TBIs_org, .) %>%
  
  # filter(ST=="MA") %>%
  
  ## Impute the missing rates, by calculating the projected number of
  ## deaths. If that's over 20, round down (since we know that can't
  ## be the case). Then, calculate the crude mortality rate
  mutate(Deaths     = if_else(imputed, round(Population*rate_miss), Deaths),
         OverEst    = if_else(imputed & Deaths > 20, TRUE, FALSE),
         Deaths     = if_else(imputed & Deaths > 20, 20, Deaths),
         Crude_Rate = 100000*Deaths/Population) %>%
  
  ## Add checks and benchmarks 
  group_by(ST) %>%
  mutate(n_missing    = sum(imputed),
         prop_missing = sum(imputed)/n()) 
```


```{r}
## shapefile of imputed counties
Imputed_shp <- US_counties %>%
  geo_join(rename(TBI_imputed, GEOID=CountyFIPS), by="GEOID") %>%
  filter(imputed)

Fig_impute <- US_counties %>%
  # filter(STATEFP=="48") %>%
  geo_join(rename(TBI_imputed, GEOID=CountyFIPS), by="GEOID") %>%
  left_join(select(df_full, GEOID, region, division)) %>%
  # filter(region %in% c("WEST","MIDWEST")|ST=="TX") %>%
  ggplot() +
  geom_sf(data = US_states, fill=NA, color="black") +
  geom_sf(aes(fill=scales::squish(Crude_Rate, range=c(0,70))), color=NA) + 
  geom_sf(data = Imputed_shp, fill="grey", color=NA, alpha=0.65) +
  
  coord_sf(crs = 4269) +
  scale_fill_distiller(palette="RdYlGn", guide = 'legend',
                       na.value = "grey50",
                       breaks = c(10,20,40,60),
                       # values=scales::rescale(quantile(TBI_imputed$Crude_Rate)),
                       values=scales::rescale(quantile(scales::squish(df$Crude, range=c(0,70)))),
                       name="TBI Mortality Rate\n(per 100,000)", direction=-1) +
  # theme_dark()
  ggthemes::theme_map() +
  theme(legend.direction="horizontal") +
  labs(title = "[Fig 4] IMPUTED TBI Mortality Rates",
       caption="Imputed counties are greyed out")

Fig_impute
```







```{r, eval=F}

summary(fit)
car::Anova(fit,type="III")

bind_cols(
  tidy(fit),
  broom::confint_tidy(fit)
)[2,]



## Who has provider?
df_full %>% mutate(hasProv = ifelse(dist_min==0, T,F)) %>% count(hasProv) %>% mutate(`%`=n/sum(n))

df_full %>% ggplot(aes(x=Urbanization, y=dist_cent)) + geom_violin()


## compare groups
df_full %>% mutate(hasProv = ifelse(dist_min==0, "Yes","No")) %>%
  t.test(Over65~hasProv, data=.)

df_full %>% mutate(hasProv = ifelse(dist_min==0, "Yes","No")) %>%
  t.test(male~hasProv, data=.)

df_full %>% mutate(hasProv = ifelse(dist_min==0, "Yes","No")) %>%
  xtabs(~hasProv+Urbanization, data=.)  %T>%
  print() %>% 
  fisher.test()


df_full %>% mutate(hasProv = ifelse(dist_min==0, "Yes","No")) %>%
  t.test(Crude~hasProv, data=.)



df_full %>% mutate(hasProv = ifelse(dist_min==0, "Yes","No")) %>%
  xtabs(~hasProv+region, data=.)  %T>%
  print() %>% 
  fisher.test()
  # chisq.test()
```










```{r OldTable2, results='asis', eval=F, include=F}
options(qwraps2_markup = "markdown")
df_compare_missing <- df_full %>%
  anti_join(df) %>%
  mutate(Exclude = T) %>%
  bind_rows(df) %>%
  mutate(Exclude = replace_na(Exclude, F)) %>%
  group_by(Exclude) 

df_compare_missing %>%
  group_by(Exclude) %>%
  
summary_table(
  list("Distance (miles)" =
         list("Mean (SD)"    = ~ qwraps2::mean_sd(.data$dist_cent, denote_sd = "paren"),
              "Median (IQR)" = ~ qwraps2::median_iqr(.data$dist_cent)),
       "Population" =
              list("Mean (SD)"    = ~ qwraps2::mean_sd(.data$StdPop, digits=0, denote_sd = "paren"),
                   "Median (IQR)" = ~ qwraps2::median_iqr(.data$StdPop, digits=0)),
       "Urbanization" = 
         list("Metro"     = ~ qwraps2::n_perc0(.data$Urbanization == "Metro"),
              "Nonmetro"  = ~ qwraps2::n_perc0(.data$Urbanization == "Nonmetro"),
              "Rural"     = ~ qwraps2::n_perc0(.data$Urbanization == "Rural")),
       "% Male" = 
         list("Mean (SD)" = ~ qwraps2::mean_sd(.data$male*100, denote_sd = "paren")),
       "% 65 or older" = 
         list("Mean (SD)" = ~ qwraps2::mean_sd(.data$Over65*100, denote_sd = "paren"))
   )
)
```



```{r nsg_bin, include=F}
nsg_bin <- df %>%
  mutate(bins = cut(num_provs, 
                    breaks = c(0,1,6,11, 200),
                    labels = c("0", "1-5", "6-10", ">10"),
                    right=F)) %>%
  group_by(bins) %>%
  summarise(n = n(),
            mean_sd = mean_sd(Crude)) %>%
  rename(NSG_in_county=bins)

nsg_bin_anova <- df %>%
  mutate(bins = cut(num_provs, 
                    breaks = c(0,1,6,11, 200),
                    labels = c("0", "1-5", "6-10", ">10"),
                    right=F)) %>%
  aov(Crude~bins, data=.)

car::Anova(nsg_bin_anova, type="III")
```


Mortality rates also varied by the number of neurosurgeons in the county (**Table 2**), with counties lacking any neurosurgeons having a mean rate $\pm$ SD of `r nsg_bin$mean_sd[1]`, counties with `r nsg_bin$NSG_in_county[2]` neurosurgeons having a rate of `r nsg_bin$mean_sd[2]`, counties with `r nsg_bin$NSG_in_county[3]` neurosurgeons having a rate of `r nsg_bin$mean_sd[3]`, and counties with `r nsg_bin$NSG_in_county[4]` neurosurgeons having a rate of `r nsg_bin$mean_sd[4]` (p < 0.001).

TABLE 4

```{r Table4, eval=F}
 tb2a <- df %>%
    group_by(Urbanization) %>%
  summarise(n = n(),
            Crude = str_glue("{round(mean_ci(Crude, na_rm = T),2)[1]} ({round(mean_ci(Crude, na_rm = T),2)[2]}, {round(mean_ci(Crude, na_rm = T),2)[3]})"),
            AgeAdj = str_glue("{round(mean_ci(AgeAdj, na_rm = T),2)[1]} ({round(mean_ci(AgeAdj, na_rm = T),2)[2]}, {round(mean_ci(AgeAdj, na_rm = T),2)[3]})")) %>%
  mutate(category = "Urbanization") %>%
  select(category, level=Urbanization, n, Crude, AgeAdj)

tb2b <- df %>%
    mutate(bins = cut(num_provs, 
                    breaks = c(0,1,6,11, 200),
                    labels = c("0", "1-5", "6-10", ">10"),
                    right=F)) %>%
  group_by(bins) %>%
  summarise(n = n(),
            Crude = str_glue("{round(mean_ci(Crude, na_rm = T),2)[1]} ({round(mean_ci(Crude, na_rm = T),2)[2]}, {round(mean_ci(Crude, na_rm = T),2)[3]})"),
            AgeAdj = str_glue("{round(mean_ci(AgeAdj, na_rm = T),2)[1]} ({round(mean_ci(AgeAdj, na_rm = T),2)[2]}, {round(mean_ci(AgeAdj, na_rm = T),2)[3]})")) %>%
  mutate(category = "NSG_in_county") %>%
  select(category, level=bins, n, Crude, AgeAdj)

bind_rows(tb2a, tb2b)
rm(rate_overall, rate_urban, nsg_bin, tb2a, tb2b)
```

```{r}
rate_needed <- df_full %>%
  # anti_join(df) %>%
  filter(is.na(Deaths)) %>%
  mutate(RateNeeded = 100000*20/StdPop) 


rate_needed$pred_rate <- predict(base_fit, rate_needed)

rate_needed %>%
  mutate(pred_deaths = pred_rate*StdPop/100000) %>%
  mutate(OverPredict = pred_deaths > 20) %>%
  count(OverPredict)

  # ggplot(aes(x=pred_deaths)) +
  # geom_density()


rate_needed %>%
  # count(OverEstimate)
  ggplot(aes(x=pred_rate, y=RateNeeded)) + 
  geom_jitter()


```



