---
title: "Regressions"
author: "Hunter Ratliff"
date: "2/10/2020"
output:
  html_document:
    df_print: paged
    code_folding: show
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=F, warning=F, message=F)
library(plotly)
library(crosstalk)
library(tidyverse)
library(ggthemes)
library(scales)
library(broom)
library(pander)  # for pretty outputs
```

# Set up

## Read in the data

Reading in `Data/mergedToTBI_v2.csv`, and dropping any varaibles with NA's

```{r readData}
df_full <- read_csv("Data/mergedToTBI_v2.csv") %>%
  select(-npi, -providerCity, -providerST) %>%
  select(GEOID:Crude) %>%
  filter(!is.na(Deaths)) %>% # drop counties with missing rates
  filter(GEOID != "46102") # GEOID didn't match to ACS data

# # Missing data
# is.na(df_full) %>% colSums()

glimpse(df_full)
```

## Plotly function

Here's a wrapper that I made that makes a pretty _Residual vs Fitted_ and _QQ plots_ plot using plotly. It takes a fitted lm model (`lm_fit`) and uses plotly to return pretty diagnostic plots, similar to if you were to run plot(lm_fit). 

```{r dx_plots, echo=T}
dx_plots <- function(lm_fit, raw_data, plots=1, alpha=.25, use_plotly=T) {
  ## lm_fit:   Fitted lm model
  ##
  ## raw_data: The data suppied to the fitted lm model. 
  ##        !! NOTE: Each observation in this needs to match it's row in the
  ##                 model matrix, so if the lm call is dropping any NA's
  ##                 you need to drop them too before passing it to this function
  ##
  ## plots:   Which plot to return: 
  ##            1 = Residual vs Fitted
  ##            2 = QQ plot
  ##            3 = Scale-location
  ##
  ## alpha:      Alpha value passed to ggplot (for dense plots)
  ## use_plotly: Logical flag to return interactive plotly object. Defaults to
  ##             true, but can change to false to cutdown on overhead/file size
  
  if(nrow(raw_data)!=nrow(model.matrix(lm_fit))){
    return("Model matrix doesn't match suppiled data")
  }
  
  ## Give unique ID for each regression, that way crosstalk
  #  can link plots from the same regression
  crosstalk_id <- str_c(lm_fit[["terms"]], collapse = "")
  
  ## augment the data with results of regression
  df_fit <- broom::augment(lm_fit, raw_data) %>%
    mutate(tooltip = str_glue("{NAME}, {ST}\nPredicted: {round(.fitted,1)}\nActual: {round(Crude,1)}\n\n")) %>%
    mutate(hasProvider = dist_min==0) %>%
    highlight_key(~tooltip, group="crosstalk_id")
  
  ## Residual vs Fitted
  p1 <- df_fit %>%
    ggplot(aes(x=.fitted, y=.resid)) + 
    geom_hline(yintercept=0, color="red") +
    geom_jitter(alpha=alpha, aes(text=tooltip, color=hasProvider)) +
    geom_smooth(se=F) +
    labs(title="Residual vs Fitted") +
    theme_bw()
  
  ## Normal Q-Q
  p2 <- df_fit %>%
    ggplot(aes(sample=.std.resid)) +
    geom_qq(alpha=alpha) +
    geom_qq_line() +
    labs(title="Normal QQ") +
    theme_bw()
  
  ## Scale-Location
  p3 <- df_fit %>%
      ggplot(aes(x=.fitted, y=sqrt(abs(.std.resid)))) + 
      geom_point(alpha=alpha, aes(text=tooltip, color=hasProvider)) +
      geom_smooth(se=F) +
      labs(title="Scale-Location") +
      theme_bw()
  
  
  if(use_plotly){
    # pass tp plotly
    if(plots==1) return(plotly::ggplotly(p1, tooltip=c("text", "x", "y")))
    if(plots==2) return(plotly::ggplotly(p2, tooltip=c("text", "x", "y")))
    if(plots==3) return(plotly::ggplotly(p3, tooltip=c("text", "x", "y")))
  } else({
    if(plots==1) return(p1)
    if(plots==2) return(p2)
    if(plots==3) return(p3)
  })
  
}
```

# Model 1

Simple linear regression

```{r def-fit1, echo=T}
fit <- lm(Crude ~ dist_cent, data=df_full)
```

```{r}
summary(fit) %>% pander()
```


```{r}
dx_plots(fit, df_full, plots = 1)
dx_plots(fit, df_full, plots = 3)
```

Sorted by top Cook's distance

```{r}
broom::augment(fit, df_full) %>%
  mutate(NAME = str_glue("{NAME}, {ST}")) %>%
  select(-ST, -Over75, -Deaths, -AgeAdj) %>%
  arrange(desc(.cooksd)) %>%
  mutate_if(is.numeric, round, 2) %>%
  select(GEOID, NAME, .cooksd, everything())
```




# Model 2

```{r def-fit2, echo=T}
fit <- lm(Crude ~ dist_cent + log(pop12) + male + Over65, data=df_full)
```

```{r}
summary(fit) %>% pander()
```


```{r}
dx_plots(fit, df_full, plots = 1, use_plotly=F)
dx_plots(fit, df_full, plots = 3, use_plotly=F)
dx_plots(fit, df_full, plots = 2, use_plotly=F)
```

Sorted by top Cook's distance

```{r}
broom::augment(fit, df_full) %>%
  mutate(NAME = str_glue("{NAME}, {ST}")) %>%
  select(-ST, -Over75, -Deaths, -AgeAdj) %>%
  arrange(desc(.cooksd)) %>%
  mutate_if(is.numeric, round, 2) %>%
  select(GEOID, NAME, .cooksd, everything())
```

## Excluding influential points

```{r def-fit2-2, echo=T}
df <- df_full %>%
  filter(!GEOID %in% c("38053","20055","30085","12119"))
fit <- lm(Crude ~ dist_cent + log(pop12) + male + Over65, data=df)
```

```{r}
summary(fit) %>% pander()
```


```{r}
dx_plots(fit, df, plots = 1)
dx_plots(fit, df, plots = 3)
dx_plots(fit, df, plots = 2, use_plotly=F)
```
Sorted by top Cook's distance

```{r}
broom::augment(fit, df) %>%
  mutate(NAME = str_glue("{NAME}, {ST}")) %>%
  select(-ST, -Over75, -Deaths, -AgeAdj) %>%
  arrange(desc(.cooksd)) %>%
  mutate_if(is.numeric, round, 2) %>%
  select(GEOID, NAME, .cooksd, everything())
```

# experimental

## Mapping residuals

```{r, cache=TRUE}
library(sf) # newer, better version of sp
library(tigris)
library(leaflet)
options(tigris_class = "sf")
options(tigris_use_cache = T)

US_counties <- tigris::counties(state = c(state.abb, "DC"), cb=T) %>%
  filter(STATEFP!="02", STATEFP!="15")

broom::augment(fit, df) %>%
  mutate(NAME = str_glue("{NAME}, {ST}")) %>%
  select(-ST, -Over75, -Deaths, -AgeAdj) %>%
  geo_join(US_counties, ., by="GEOID") %>%
  ggplot() +
  geom_sf(aes(fill=.resid), color=NA) + 
  coord_sf(crs = 4269) +
  scale_fill_distiller(palette="RdYlGn",# guide = 'legend',
                       na.value = "grey50",
                       name="Residuals", direction=1) +
  # theme_dark()
  ggthemes::theme_map() +
  theme(legend.direction="horizontal") 
```


## Using ggiraph & cowplot

Very slow

```{r ggiraph, eval=F}
fit <- lm(Crude ~ dist_cent + ST + log(pop12) + male + Over65, data=df_full)
fit_df <- broom::augment(fit, data=filter(df_full, !is.na(Crude), !is.na(pop12)))
library(ggiraph)
library(cowplot)



## Residual vs Fitted
tictoc::tic()
p1 <- fit_df %>%
  ggplot(aes(x=.fitted, y=.resid)) + 
  geom_hline(yintercept=0, color="red") +
  geom_point_interactive(aes(tooltip = NAME, data_id = GEOID),alpha=.15) +
  # geom_jitter(alpha=.5) +
  geom_smooth(se=F) +
  labs(title="Residual vs Fitted") +
  theme_bw()


## Scale-Location
p2 <- fit_df %>%
  ggplot(aes(x=.fitted, y=sqrt(abs(.std.resid)))) + 
  geom_point_interactive(aes(tooltip = NAME, data_id = GEOID),alpha=.15) +
  # geom_point(alpha=.5) +
  geom_smooth(se=F)


girafe(ggobj = plot_grid(p1,p2))
tictoc::toc()
rm(p1, p2)
```

## Using plotly and crosstalk

```{r crosstalk, eval=F}
fit <- lm(Crude ~ dist_cent + ST + log(pop12) + male + Over65, data=df_full)
library(crosstalk)
fit_df <- broom::augment(fit, data=filter(df_full, !is.na(Crude), !is.na(pop12))) %>%
  highlight_key(~GEOID, group="mytestgroup")

library(plotly)
## Residual vs Fitted
tictoc::tic()
p1 <- fit_df  %>% 
    ggplot(aes(x=.fitted, y=.resid)) + 
    geom_hline(yintercept=0, color="red") +
    geom_jitter(alpha=.5) +
    geom_smooth(se=F) +
    labs(title="Residual vs Fitted") +
    theme_bw()

p2 <- fit_df %>%
  ggplot(aes(sample=.std.resid)) +
  geom_qq() +
  geom_qq_line() +
  labs(title="Normal QQ") +
  theme_bw()
   
## Scale-Location
p3 <- fit_df %>%
    ggplot(aes(x=.fitted, y=sqrt(abs(.std.resid)))) + 
    
    geom_point(alpha=.5) +
    geom_smooth(se=F) +
    labs(title="Scale-Location") +
    theme_bw()
  

subplot(ggplotly(p1, tooltip = "GEOID"), 
        ggplotly(p2, tooltip = "GEOID"), 
        titleX = T, titleY = T)
tictoc::toc()
rm(p1, p2)
```

```{r crosstalk2, eval=F}
library(crosstalk)


df <- mtcars %>%
  rownames_to_column(var="carname") %>%
  select(carname, mpg, cyl, hp, wt)

p1 <- df %>%
  # must use group="testgroup", so it will share the crosstalk
  highlight_key(~carname, group="testgroup") %>% {
    ggplot(., aes(wt, hp, group = carname)) + geom_point()
  } %>%
  ggplotly(tooltip = "carname")

p2 <- df %>%
  highlight_key(~carname, group="testgroup") %>% {
    ggplot(., aes(wt, mpg, group = carname)) + geom_point()
  } %>%
  ggplotly(tooltip = "carname")

subplot(p1, p2, titleX = T, titleY = T)
rm(p1,p2,df)
```

```{r, eval=F}


df <- df_full %>%
  select(Crude, dist_cent, pop12, male, Over75)
lm(Crude ~ dist_cent, data=df) %>% summary()

lm(Crude ~ dist_cent + log(pop12) , data=df)



fit <- lm(Crude ~ dist_cent, data=df_full)

## Residual vs Fitted
fit_df %>%
  ggplot(aes(x=.fitted, y=.resid, tooltip = NAME, data_id = GEOID)) + 
  geom_hline(yintercept=0, color="red") +
  geom_point_interactive(aes(tooltip = NAME, data_id = GEOID),alpha=.15) +
  # geom_jitter(alpha=.5) +
  geom_smooth(se=F) +
  labs(title="Residual vs Fitted") +
  theme_bw()

## Normal Q-Q
# car::qqp(fit)
fit_df %>%
  ggplot(aes(sample=.std.resid)) +
  geom_qq() +
  geom_qq_line() +
  labs(title="Normal QQ") +
  theme_bw()

## Scale-Location
fit_df %>%
  ggplot(aes(x=.fitted, y=sqrt(abs(.std.resid)))) + 
  geom_point(alpha=.5) +
  geom_smooth(se=F)




# plot(fit)
```
