---
title: "Working with geodata"
author: "Hunter Ratliff"
date: "1/24/2020"
output:
  html_document:
    df_print: paged
    code_folding: show
    toc: true
    toc_float: true
---

    



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=T, warning=F, message=F)

library(testthat)
library(magrittr)
library(ggmap)
library(viridis)
library(tictoc)
library(RColorBrewer)
library(rgeos)
library(spdep)
library(sp)
library(maps)
library(maptools)
library(sf) # newer, better version of sp
library(tigris)
library(leaflet)
library(tidycensus)
library(tidyverse)

options(tigris_class = "sf")
options(tigris_use_cache = TRUE)
```

# Read in data & transform

Spatial data in R is not my strong suit, so these articles helped me get to where I am (and might be helpful in the future for debugging):

- [Plotting "Spatial" data with ggplot](https://eriqande.github.io/rep-res-eeb-2017/plotting-spatial-data-with-ggplot.html) Very good resource
- [Mapping using ggplot2](http://zevross.com/blog/2014/07/16/mapping-in-r-using-the-ggplot2-package/)
- [Plotting polygons](https://github.com/tidyverse/ggplot2/wiki/plotting-polygon-shapefiles) using `geom_polygon` and `fortify(Spatial*Polygons*DataFrame)`

## Projections & coordinates


Per the linked website [above](https://mgimond.github.io/Spatial/coordinate-systems-in-r.html#understanding-the-proj4-coordinate-syntax), there are two ways of defining a coordinate system: via the EPSG numeric code or via the PROJ4 formatted string. All spatial objects with defined coordinate systems will always have a PROJ4 projection string, but not all will have a EPSG numeric code. 

When we read in the county level polygons (using tigris / tidycensus) it returns objects with a class of `sf` that use the following Coordinate Reference System:

- EPSG: 4269 
- proj4string: "+proj=longlat +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +no_defs"

When these are coerced to sp objects the EPSG gets dropped

## Creating sf objects

We can grab the geomety of the counties using the **tigris** package or use **tidycensus** package to grab the population estimates along with the tigris shapes. Both return objects with the classes "sf" "data.frame"

```{r getCounties, collapse=T}
# Counties w/ population
countyPop <- tidycensus::get_acs(geography = "county", geometry = T,
                                 state = "TX", 
                                 variables = "B01001_001")
class(countyPop)


# using tigris alone
counties <- tigris::counties(state = "TX", cb=T)
class(counties)
rm(counties)
```

To create the points for each provider we can also make a sf object from the tibble. When we do this, we need to specify the CRS (coordinate reference system) by supplying it with the same CRS as we are using in the county files^[You can reterieve the CRS with `sf::st_crs()`]. 

```{r}
# Geocoded from API
geo_raw <- read_csv("Google_results/geo_google_raw.csv")
glimpse(geo_raw)

# Make sf object
TX_providers <- geo_raw %>%
  filter(geoState=="tx") %>%
  st_as_sf(coords = c("lon", "lat"), crs=4269)
class(TX_providers)

# Same CRS?
st_crs(TX_providers) == st_crs(counties)
```


#### Going from sf to sp

sf objects can easily be converted to their sp counterparts (SpatialXXXDataFrame) using `sf::as_Spatial()`. Notably, this transformation drops the EPSG code

```{r SFtoSP, eval=F}
## NOT RUN

## sf --> Spatial POLYGONS Data Frame
countyPop %>% 
  sf::as_Spatial(IDs = countyPop$GEOID) %>%
  class()


## sf --> Spatial POINTS Data Frame
TX_providers %>%
  sf::as_Spatial(IDs = TX_providers$npi) %>%
  class()


## sp object can be brought back with st_as_sf()
tx_sp <- TX_providers %>% sf::as_Spatial()
st_as_sf(tx_sp)  # must reassign CRS !
```









# Plotting

Using ggplot with sf objects is easy. It's a bit harder with sp

```{r plot1}
ggplot() + 
  geom_sf(data=countyPop) +
  geom_sf(data=TX_providers) +
  coord_sf(crs = 4269)


# countyPop %>%
#   filter(str_detect(NAME, ", Texas")) %>%
#   ggplot(aes(fill = estimate, color = estimate)) +
#   geom_sf() +
#   coord_sf(crs = 4269)
```


# Distance calculation

The function below, `find_closest()` takes two arguments, both sf files. The first argument (`county_sf`) should be the geometries of the counties^[It'll throw an error if the geometry isn't a multipolygon] and the second (`prov_sf`) a sf object with the points of the providers.

This function works in two main steps. First, for each feature/geometry (i.e. county) in `county_sf`, it finds the nearest point (i.e. provider) in `prov_sf`. It then calculates the distance from the identified provider to the county. If the centroid flag is TRUE (default), it calculates the distance from the provider to the centroid of the county. Otherwise, it finds the minimum distance from the edge of the county to the provider identified in the first step^[This has the added benifit of marking counties that have a provider anywhere within the county as having a distance of 0 miles].

Please note that in the first step, this function finds the closest provider **based on the closest edge of the county**. It behaves this way **REGARDLESS of the centroid flag**.


```{r closestFxn}
find_closest <- function(county_sf, prov_sf, centroid=T) {
  
  tic() # time the function
  library(testthat)
  
  test_that("inputs are sf objects", {
    expect_s3_class(county_sf, "sf")
    expect_s3_class(prov_sf, "sf")
  })
  
  test_that("Correct geometries", {
    county_sf_geo <- as.character(st_geometry_type(county_sf)[[1]])
    expect_equal(county_sf_geo, "MULTIPOLYGON")
    prov_sf_geo <- as.character(st_geometry_type(prov_sf)[[1]])
    expect_equal(prov_sf_geo, "POINT")
  })
  
  
  
  
  # Finds index of nearest provider for each county
  i <- st_nearest_feature(county_sf, prov_sf)
  p <- prov_sf[i,]
  
  # Calculate distance for each element
  if(centroid){
    
    distance <- st_distance(p, st_centroid(county_sf), by_element=T)
  } else({
    
    distance <- st_distance(p, county_sf, by_element=T)
  })
  
  
  # Create a data frame with results
  df <- tibble(
    GEOID         = county_sf$GEOID,
    npi           = p$npi,
    providerCity  = p$geoCity,
    providerST    = p$geoState,
    Distance      = units::set_units(distance, mi),
    Distance_m    = distance
  ) %>%
  mutate(
    Distance = as.numeric(Distance)
  )
  
  # Join to county_sf to make sf object
  df_sf <- geo_join(county_sf, df, by="GEOID") 
  
   
  toc() # end timer
  return(df_sf)
}
```

```{r loadData}
geo_raw <- read_csv("Google_results/geo_google_raw.csv")

multiCounties <- tigris::counties(state = state.abb, cb=T) %>%
  filter(STATEFP!="02", STATEFP!="15")

provs <- geo_raw %>%
  filter(geoState!="hi", geoState!="ak") %>%
  st_as_sf(coords = c("lon", "lat"), crs=4269)

TBIs <- read_csv("Data/TBI_Deaths.csv")
```

```{r, eval=F}
# takes around 20 sec to run
df <- find_closest(multiCounties, provs, centroid = F) %>%
  select(STATEFP, GEOID, NAME, npi:Distance_m, geometry)
glimpse(df)
```


```{r, eval=F}
# can take up to 60 seconds to render map
df %>% 
  ggplot() + 
  geom_sf(aes(fill = Distance), color=NA) +
  geom_sf(data=provs, alpha=0.25) +
  coord_sf(crs = 4269) +
  scale_fill_distiller(palette="Reds", guide = 'legend',
                       trans="sqrt",
                       name="Mi to nearest NSG", direction=1) +
  theme(legend.direction="horizontal",legend.position=c(0.5,0)) +
  ggthemes::theme_map() +
  theme(legend.direction="horizontal")
```

### Correlation

```{r, eval=F}
df %>%
  inner_join(TBIs, by=c("GEOID"="CountyFIPS")) %>%
  mutate(PercTBI = percent_rank(Crude_Rate)) %>%
  filter(!is.na(PercTBI)) %>%
  as.data.frame() %$%
  cor(Distance, Crude_Rate)
  # cor.test(~Crude_Rate+Distance, data=.)

df %>%
  inner_join(TBIs, by=c("GEOID"="CountyFIPS")) %>%
  mutate(PercTBI = percent_rank(Crude_Rate)) %>%
  filter(!is.na(PercTBI)) %>%
  as.data.frame() %>%
  glm(Crude_Rate~sqrt(Distance), data=., family = gaussian(link = "log")) %>%
  # lm(Crude_Rate~sqrt(Distance), data=.) %>%
  plot()
  summary()
  
```


## Making arrows

```{r, eval=F, include=F}
# to create lines manually:
cbind(c(0,0,1,2), c(3,4,5,5)) %>% st_linestring() %>% plot()
```

```{r, eval=F}

tigris::counties(state = "TX", cb=T) %>%
  find_closest(provs, centroid = T) %>%
  # View()
  # left_join(geo_raw) %>%
  # select(GEOID, NAME, npi:Distance, lon, lat, geometry) %>%
  ggplot() +
  geom_sf(aes(fill=Distance), color=NA) +
  geom_sf(data=TX_providers, alpha=0.25) +
  # geom_point(aes(lat, lon)) + # not working
  coord_sf(crs = 4269) +
  scale_fill_distiller(palette="Reds", guide = 'legend',
                       # values = c(0,.25,1),
                       trans="sqrt",
                       name="Mi to nearest NSG", direction=1) +
  theme(legend.direction="horizontal",legend.position=c(0.5,0)) +
  ggthemes::theme_map()
```







```{r DistUsingSP, eval=F}
proj_str <- st_crs(TX_providers)$proj4string  # Use same projection as our current map

# Get a few counties
county_sf <- counties %>%
  filter(NAME%in% c("Galveston", "Lubbock", "Travis", "Bexar", "Dallas")) 
county_sp <- county_sf %>%
  as_Spatial()
proj4string(county_sp) <- CRS(proj_str)

# Select 3 random providers in TX
prov_sf <- TX_providers %>% 
  filter(npi %in% c(1578894267, 1154764728, 1144317157)) 
prov_sp <- prov_sf %>%
  sf::as_Spatial()
proj4string(prov_sp) <- CRS(proj_str)


DistMat <- rgeos::gDistance(prov_sp, county_sp, byid=T)
rownames(DistMat) <- county_sp@data[["NAME"]]
colnames(DistMat) <- prov_sp@data[["geoCity"]]
DistMat
{plot(county_sp)
plot(prov_sp, add=T)}

rm(county_sp, prov_sp, DistMat)
```



```{r, eval=F}
pts <- locator(5,type="p")
geosphere::dist2Line(p = SpatialPoints(pts), line = TX)

pts2 <- sp::makegrid(wrld_simpl, n = 5)
apply(rgeos::gDistance(SpatialPoints(pts, proj4string=CRS(proj4string(TX))), TX,byid=TRUE),2,min)
```

